---
title: "Untitled"
author: "Felicia Zhang"
date: '2018-01-24'
output: html_document
---

```{r setup, include=FALSE}
library(ggplot2) 
library(zoo)
library(reshape)
library(plyr)
library(dplyr)
library(scales) 
library(data.table)
library(signal)
library(matrixStats)
library(lme4)
library(arm)
library(RColorBrewer)
library(lmerTest)
library(boot)

#load preprocessed data
orig.sample2 <- read.csv("/Volumes/emberson/ResearchProjects/Pupillometry/Pinwheels/Data/Pinwheel_Infant_Preprocessed_RemovedOutliers_Nov28.csv")  #Nov28 has bad trials removed
orig.sample2$X <- NULL
orig.sample2$X.1 <- NULL

#recode trial number
orig.sample2$trialnum <- 0
orig.sample2$trialnum[orig.sample2$TRIAL_INDEX == 1 | orig.sample2$TRIAL_INDEX == 9 | orig.sample2$TRIAL_INDEX == 17 | orig.sample2$TRIAL_INDEX == 25 | orig.sample2$TRIAL_INDEX == 33 | orig.sample2$TRIAL_INDEX == 41] <- 1
orig.sample2$trialnum[orig.sample2$TRIAL_INDEX == 2 | orig.sample2$TRIAL_INDEX == 10 | orig.sample2$TRIAL_INDEX == 18 | orig.sample2$TRIAL_INDEX == 26 | orig.sample2$TRIAL_INDEX == 34 | orig.sample2$TRIAL_INDEX == 42] <- 2
orig.sample2$trialnum[orig.sample2$TRIAL_INDEX == 3 | orig.sample2$TRIAL_INDEX == 11 | orig.sample2$TRIAL_INDEX == 19 | orig.sample2$TRIAL_INDEX == 27 | orig.sample2$TRIAL_INDEX == 35 | orig.sample2$TRIAL_INDEX == 43] <- 3
orig.sample2$trialnum[orig.sample2$TRIAL_INDEX == 4 | orig.sample2$TRIAL_INDEX == 12 | orig.sample2$TRIAL_INDEX == 20 | orig.sample2$TRIAL_INDEX == 28 | orig.sample2$TRIAL_INDEX == 36 | orig.sample2$TRIAL_INDEX == 44] <- 4
orig.sample2$trialnum[orig.sample2$TRIAL_INDEX == 5 | orig.sample2$TRIAL_INDEX == 13 | orig.sample2$TRIAL_INDEX == 21 | orig.sample2$TRIAL_INDEX == 29 | orig.sample2$TRIAL_INDEX == 37 | orig.sample2$TRIAL_INDEX == 45] <- 5
orig.sample2$trialnum[orig.sample2$TRIAL_INDEX == 6 | orig.sample2$TRIAL_INDEX == 14 | orig.sample2$TRIAL_INDEX == 22 | orig.sample2$TRIAL_INDEX == 30 | orig.sample2$TRIAL_INDEX == 38 | orig.sample2$TRIAL_INDEX == 46] <- 6
orig.sample2$trialnum[orig.sample2$TRIAL_INDEX == 7 | orig.sample2$TRIAL_INDEX == 15 | orig.sample2$TRIAL_INDEX == 23 | orig.sample2$TRIAL_INDEX == 31 | orig.sample2$TRIAL_INDEX == 39 | orig.sample2$TRIAL_INDEX == 47] <- 7
orig.sample2$trialnum[orig.sample2$TRIAL_INDEX == 8 | orig.sample2$TRIAL_INDEX == 16 | orig.sample2$TRIAL_INDEX == 24 | orig.sample2$TRIAL_INDEX == 32 | orig.sample2$TRIAL_INDEX == 40 | orig.sample2$TRIAL_INDEX == 48] <- 8

#excluded trial 1 of each preswitch sub-block
orig.sample3 <- subset(orig.sample2, !(switch==1 & trialnum==1))

#counting number of babies for criteria 3: contribute at least one trial for 4/6 subblock (2 for preswitch and 2 for postswitch)
#exclude: 3, 4, 16, 19, 22, 27, 29, 30 (8 subs excluded)
orig.sample4 <- subset(orig.sample3, subID != 3)
orig.sample4 <- subset(orig.sample4, subID != 4)
orig.sample4 <- subset(orig.sample4, subID != 16)
orig.sample4 <- subset(orig.sample4, subID != 19)
orig.sample4 <- subset(orig.sample4, subID != 22)
orig.sample4 <- subset(orig.sample4, subID != 27)
orig.sample4 <- subset(orig.sample4, subID != 29)
orig.sample4 <- subset(orig.sample4, subID != 30)

#orig.sample2 = trials with more than 50% looking
#orig.sample3 = excluded trial 1 of each preswitch sub-block
#orig.sample4 = excluded subjects
```

AEM coding
```{r}
poo <- orig.sample4

#1. Binning every 100ms, to make sure that it's actually a fixation for lookstotarget
moo <- data.frame(subID=numeric(),trialnum=numeric(),timecode=numeric(),block=numeric(),switch=numeric(),lookingattarget=numeric())
subs <- unique(poo$subID)
time <- seq(100,4000, by=100) #the time bins we are trying to create (0-4000ms) doing 4000ms 

for (j in 1:length(subs)) {
  #gets every trial for 1 subject
  trials <- unique(poo$TRIAL_INDEX[poo$subID==subs[j]])
  print(j)
  for (i in 1:length(trials)) {
    #gets all sample for 1 trial  
    woo <- subset(poo, subID==subs[j] & TRIAL_INDEX == trials[i])
    c <- woo$block[1]
    cc <- woo$switch[1]
    ccc <- woo$trialnum[1]
    for (k in 1:length(time)){
      #for every 25 sample/100 ms, get lookattarget column
      if (k==1) {
        target <- woo$lookattarget[woo$TIMECODE < time[k]+1] #gets 0-100ms
        d <- unique(target)
        dd <- which(d==1)
      } else {
        target <- woo$lookattarget[woo$TIMECODE < time[k]+1 & woo$TIMECODE > time[k-1]-1]
        d <- unique(target)
        dd <- which(d==1)
      }
      #see if entire chunk is looking at target
      if (length(target)==0) { #no samples collected during this time
        aa <- c(subs[j],trials[i],ccc,c,cc,time[k],99)   
        moo <- rbind(moo,aa)
        warnings()
      } else if (length(d)==1 & d==1) { #looking at target entire time
        aa <- c(subs[j],trials[i],ccc,c,cc,time[k],d)   
        moo <- rbind(moo,aa)
        warnings()
      } else if (length(d)==1 & d==0) { #looking at distractor entire time
        aa <- c(subs[j],trials[i],ccc,c,cc,time[k],d)   
        moo <- rbind(moo,aa)
        warnings()
      } else if (length(d)==1 & d==5) { #looking at center entire time
        aa <- c(subs[j],trials[i],ccc,c,cc,time[k],d)   
        moo <- rbind(moo,aa)
        warnings()
      } else if (length(d) > 1 & length(dd) < 1) { #not looking at same location and not looking at target (looking at distractor and center)
        aa <- c(subs[j],trials[i],ccc,c,cc,time[k],9)   
        moo <- rbind(moo,aa) 
        warnings()
      } else { #not looking at same location and but looking at target sometimes
        #calculate proportion looking  
        b <- length(which(target==1)) #samples where subs are looking at target
        bb <- length(which(target==1))/length(target) #looking at target/25
        aa <- c(subs[j],trials[i],ccc,c,cc,time[k],bb) 
        moo <- rbind(moo,aa)
        warnings()
      }}}}

names(moo)[1] <- "subID"
names(moo)[2] <- "trialnum"
names(moo)[3] <- "trialnum2"
names(moo)[4] <- "block"
names(moo)[5] <- "switch"
names(moo)[6] <- "timecode"
names(moo)[7] <- "lookattarget"

#0 = distractor, 1 = target, 5 = center, 9 = looking at distractor and center, 99 = no data collected
x1 <- subset(moo, lookattarget < 99) #remove no data collected
x1$looktocenter <- 0

#coding which trials looked to center before making AEM
subs <- unique(x1$subID)
for (j in 1:length(subs)) {
  #gets every trial for 1 subject
  trials <- unique(x1$trialnum[x1$subID==subs[j]])
  print(j)
  for (i in 1:length(trials)) {
    foo <- subset(x1, subID==subs[j] & trialnum==trials[i] & timecode < 701)  
    if (any(foo$lookattarget==5)) {
      x1$looktocenter[x1$subID==subs[j] & x1$trialnum==trials[i]] <- 1
    }
  }}

#code trial type: pupil match, pupil mismatch, or no AEM 
#must look to center first, must make eye movement in 700-2700ms
#type 1 = pupil match, 2 = pupil mismatch, 3 = no AEM

x1$type <- 3
subs <- unique(x1$subID)

for (j in 1:length(subs)) {
  #gets every trial for 1 subject
  trials <- unique(x1$trialnum[x1$subID==subs[j]])
  print(j)
  for (i in 1:length(trials)) {
    #current trial
    foo <- subset(x1, subID==subs[j] & trialnum==trials[i] & timecode > 699 & timecode <2601) 
    if (any(foo$lookattarget==0) & foo$looktocenter[1]==1) {
      x1$type[x1$subID==subs[j] & x1$trialnum==trials[i]] <- 2
    }
    if (any(foo$lookattarget==1) & foo$looktocenter[1]==1) {
      x1$type[x1$subID==subs[j] & x1$trialnum==trials[i]] <- 1
    }
    }
  }

pupilbreakdown <- x1
```

add in trialtype info for orig.sample4
Recode every trial two times
- correct vs incorrect for AEM
-match vs mismatch for the pupil 

```{r}
#match vs mismatch for the pupil 
z1 <- ddply(pupilbreakdown,.(subID,trialnum,trialnum2),summarise,trialtype=(unique(type,na.rm = TRUE)))  
z1 <- subset(z1, trialtype < 3)

orig.sample4$trialtype.pupil <- 3

for (j in 1:length(z1$subID)) {
  x <- z1$subID[j]
  y <- z1$trialnum[j]
  y2 <- z1$trialnum2[j]
  z <- z1$trialtype[j]
  orig.sample4$trialtype.pupil[orig.sample4$subID==x & orig.sample4$TRIAL_INDEX==y & orig.sample4$trialnum==y2] <- z
}
#type 1 = pupil match, 2 = pupil mismatch, 3 = no AEM

#correct vs incorrect for AEM
orig.sample4$trialtype.aem <- orig.sample4$trialtype.pupil
#only trial 1 of post-switch switches labelling, unless it's 3
orig.sample4$trialtype.aem[orig.sample4$trialtype.pupil==1 & orig.sample4$trialnum==1 & orig.sample4$switch==2] <- 2
orig.sample4$trialtype.aem[orig.sample4$trialtype.pupil==2 & orig.sample4$trialnum==1 & orig.sample4$switch==2] <- 1
#type 1 = correct aem, 2 = incorrect aem, 3 = no AEM

#checking to make sure the correct trials were recoded
foo <- ddply(orig.sample4,.(subID,TRIAL_INDEX,trialtype.aem),summarise,trialtype.pupil=unique(trialtype.pupil,na.rm = TRUE))
foo$diff <- foo$trialtype.aem - foo$trialtype.pupil 
```

Recode post-switch trial 1
```{r}
orig.sample4a <- subset(orig.sample4, switch==1)
orig.sample4a <- subset(orig.sample4a, trialnum > 1)
orig.sample4a$NEWTRIALNUM <- orig.sample4a$trialnum
#2-9 for pre, 1-8 for post

orig.sample4b <- subset(orig.sample4, switch==2)
orig.sample4b$NEWTRIALNUM <- orig.sample4b$trialnum 

#relabel center and aem time period as preswitch trial 9
orig.sample4b$switch[orig.sample4b$TIMECODE < 2701 & orig.sample4b$trialnum==1] <- 1
orig.sample4b$NEWTRIALNUM[orig.sample4b$TIMECODE < 2701 & orig.sample4b$trialnum==1] <- 9

orig.sample5 <- rbind(orig.sample4a,orig.sample4b)

orig.sample5$TRIAL_INDEX[orig.sample5$switch==1 & orig.sample5$NEWTRIALNUM==9 & orig.sample5$block==1] <- 101
orig.sample5$TRIAL_INDEX[orig.sample5$switch==1 & orig.sample5$NEWTRIALNUM==9 & orig.sample5$block==2] <- 201
orig.sample5$TRIAL_INDEX[orig.sample5$switch==1 & orig.sample5$NEWTRIALNUM==9 & orig.sample5$block==3] <- 301
```

categorize babies based on % AEM , do median split 
```{r}
#categorize babies based on % AEM , do median split 
z1 <- ddply(orig.sample5,.(subID,TRIAL_INDEX),summarise,aemtrialtype=unique(trialtype.aem,na.rm = TRUE))  
#total number of trials
z3 <- ddply(z1,.(subID),summarise,trialnum=length(unique(TRIAL_INDEX,na.rm = TRUE)))

#aem trials, only want correct and incorrect
#type 1 = correct AEM to target, 2 = incorrect AEM to distractor, 3 = no AEM
z2 <- subset(z1, aemtrialtype < 3) 
#total number of AEM (correct and incorrect)  
z4 <- ddply(z2,.(subID),summarise,trialnum=length(unique(TRIAL_INDEX,na.rm = TRUE)))

#calculate percent AEM (# of AEM/# of trials)
z3$percentaem <- 0
subs <- unique(z3$subID)
for (j in 1:length(subs)) { 
z <- which(z4$subID==subs[j])
if (length(z)==0) { #if doesn't match
  z3$percentaem[j] <- NA
} else {
  z3$percentaem[j] <-z4$trialnum[z] / z3$trialnum[j]
}} 

#calculate median split
aem.med <- median(z3$percentaem, na.rm = TRUE)
which(z3$percentaem < aem.med) #2  3  7  9 11 14 20 21 22 24 25 26
which(z3$percentaem > aem.med) #1  4  5  8 10 12 13 15 16 18 19 23
orig.sample5$median.aem <- 1 #below median

#label in dataframe  
orig.sample5$median.aem[orig.sample5$subID==subs[1] | orig.sample5$subID==subs[4] | orig.sample5$subID==subs[5] | orig.sample5$subID==subs[8] |orig.sample5$subID==subs[10]| orig.sample5$subID==subs[12]| orig.sample5$subID==subs[13]|  orig.sample5$subID==subs[15]| orig.sample5$subID==subs[16]| orig.sample5$subID==subs[18]| orig.sample5$subID==subs[19]| orig.sample5$subID==subs[23]] <- 2
```

bar graph: pupil match/mismatch percentage for each subject
```{r}
#total number of trials completed by subject
w1 <- ddply(orig.sample5,.(subID,TRIAL_INDEX),summarise,pupiltrialtype=unique(trialtype.pupil,na.rm = TRUE))
w2 <- ddply(w1,.(subID),summarise,numoftrials=length(unique(TRIAL_INDEX,na.rm = TRUE)))

#grouping trials into trialtypes
w.match <- subset(w1, pupiltrialtype==1)
w.mismatch <- subset(w1, pupiltrialtype==2)
w.no <- subset(w1, pupiltrialtype==3)

#total number of trials for each trial type  
w.match2 <- ddply(w.match,.(subID),summarise,numoftrials=length(unique(TRIAL_INDEX,na.rm = TRUE)))
w.mismatch2 <- ddply(w.mismatch,.(subID),summarise,numoftrials=length(unique(TRIAL_INDEX,na.rm = TRUE)))
w.no2 <- ddply(w.no,.(subID),summarise,numoftrials=length(unique(TRIAL_INDEX,na.rm = TRUE)))

#create empty dataframe
subs <- unique(orig.sample5$subID)
goo <- data.frame(subID=numeric(78),trialtype=numeric(78),percent=numeric(78))
goo$subID <- subs
goo$trialtype <- rep(1:3, each = 26)

#calculate percent
#trialtype 1 (match)
subs <- unique(goo$subID)
for (j in 1:length(subs)) { 
z <- which(w.match2$subID==subs[j])
zz <- which(w2$subID==subs[j]) 
if (length(z)==0) { #if doesn't match
  goo$percent[j] <- NA
} else {
  goo$percent[j] <- w.match2$numoftrials[z] / w2$numoftrials[zz]
}} 

#trialtype 2 (mismatch)
subs <- unique(goo$subID)
for (j in 1:length(subs)) { 
z <- which(w.mismatch2$subID==subs[j])
zz <- which(w2$subID==subs[j]) 
if (length(z)==0) { #if doesn't match
  goo$percent[j+26] <- NA
} else {
  goo$percent[j+26] <- w.mismatch2$numoftrials[z] / w2$numoftrials[zz]
}} 

#trialtype 3 (no AEM)
subs <- unique(goo$subID)
for (j in 1:length(subs)) { 
z <- which(w.no2$subID==subs[j])
zz <- which(w2$subID==subs[j]) 
if (length(z)==0) { #if doesn't match
  goo$percent[j+52] <- NA
} else {
  goo$percent[j+52] <- w.no2$numoftrials[z] / w2$numoftrials[zz]
}} 

#plot
goo$trialtype[1:26] <- 3
goo$trialtype[53:78] <- 1
  
ggplot(goo,aes(x=factor(subID),y=percent,color=factor(trialtype),fill=factor(trialtype)))+
  geom_bar(stat="identity")+
  labs(x = "Subject", y = "% of trials")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  guides(color=FALSE)+
  scale_color_manual(values = c("#ed9c98", "#d00f29","#edbd60"))+
  scale_fill_manual(values = c("#ed9c98", "#d00f29","#edbd60"),name="Trial breakdown",breaks=c("1","2","3"),labels=c("no AEM", "pupil mismatch","pupil match"))+
  theme(legend.position = "bottom")+
  theme(panel.background = element_rect(fill = "#f5ebe1",colour = "#f5ebe1",size = 0.5, linetype = "solid"))+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank())+
  scale_y_continuous(label=percent,limits=c(0,1),breaks=seq(0,1,.2))
```

bar graph: aem correct/incorrect percentage for each subject
```{r}
#total number of trials completed by subject
v1 <- ddply(orig.sample5,.(subID,TRIAL_INDEX),summarise,aemtrialtype=unique(trialtype.aem,na.rm = TRUE))
v2 <- ddply(v1,.(subID),summarise,numoftrials=length(unique(TRIAL_INDEX,na.rm = TRUE)))

#grouping trials into trialtypes
v.cor <- subset(v1, aemtrialtype==1)
v.incor <- subset(v1, aemtrialtype==2)
v.no <- subset(v1, aemtrialtype==3)

#total number of trials for each trial type  
v.cor2 <- ddply(v.cor,.(subID),summarise,numoftrials=length(unique(TRIAL_INDEX,na.rm = TRUE)))
v.incor2 <- ddply(v.incor,.(subID),summarise,numoftrials=length(unique(TRIAL_INDEX,na.rm = TRUE)))
v.no2 <- ddply(v.no,.(subID),summarise,numoftrials=length(unique(TRIAL_INDEX,na.rm = TRUE)))

#create empty dataframe
subs <- unique(orig.sample5$subID)
moo <- data.frame(subID=numeric(78),trialtype=numeric(78),percent=numeric(78))
moo$subID <- subs
moo$trialtype <- rep(1:3, each = 26)

#calculate percent
#trialtype 1 (correct)
subs <- unique(moo$subID)
for (j in 1:length(subs)) { 
z <- which(v.cor2$subID==subs[j])
zz <- which(v2$subID==subs[j]) 
if (length(z)==0) { #if doesn't match
  moo$percent[j] <- NA
} else {
  moo$percent[j] <- v.cor2$numoftrials[z] / v2$numoftrials[zz]
}} 

#trialtype 2 (incorrect)
subs <- unique(moo$subID)
for (j in 1:length(subs)) { 
z <- which(v.incor2$subID==subs[j])
zz <- which(v2$subID==subs[j]) 
if (length(z)==0) { #if doesn't match
  moo$percent[j+26] <- NA
} else {
  moo$percent[j+26] <- v.incor2$numoftrials[z] / v2$numoftrials[zz]
}} 

#trialtype 3 (no AEM)
subs <- unique(moo$subID)
for (j in 1:length(subs)) { 
z <- which(v.no2$subID==subs[j])
zz <- which(v2$subID==subs[j]) 
if (length(z)==0) { #if doesn't match
  moo$percent[j+52] <- NA
} else {
  moo$percent[j+52] <- v.no2$numoftrials[z] / v2$numoftrials[zz]
}} 

#plot
moo$trialtype[1:26] <- 3
moo$trialtype[53:78] <- 1
  
ggplot(moo,aes(x=factor(subID),y=percent,color=factor(trialtype),fill=factor(trialtype)))+
  geom_bar(stat="identity")+
  labs(x = "Subject", y = "% of trials")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  guides(color=FALSE)+
  scale_fill_brewer(palette="Set3",name="Trial breakdown",breaks=c("1","2","3"),labels=c("no AEM", "incorrect AEMs","correct AEMs"))+
  scale_color_brewer(palette="Set3")+
  theme(legend.position = "bottom")+
  scale_y_continuous(label=percent,limits=c(0,1),breaks=seq(0,1,.2))

```

Correlation to see if correct AEM is related to pupil difference
x axis = % of correct AEMs for each baby and each block 
y axis = subtraction between the pupil of 1500-2000ms
```{r}
#1. % = correct AEM / total num of AEM

#2. % = correct AEM / total num of trials

```

Correlation to see if correct AEM is related to pupil difference
x axis = % of correct AEMs for each baby and each block 
y axis = subtraction between the pupil of 2500-4000
```{r}
#1. % = correct AEM / total num of AEM

#2. % = correct AEM / total num of trials

```

How well u do in preswitch (% correct AEM in preswitch) -> postswitch (% correct AEM in postswitch) correlation for every subject 
% correct AEM can be calculated in two ways
1. correct AEM / total num of AEM
2. correct AEM / total num of trials
```{r}
#1. % = correct AEM / total num of AEM

#2. % = correct AEM / total num of trials
```

How well u do in early postswitch (% correct AEM in trials 1-4) -> later postswitch (% correct AEM in trials 5-8) correlation for every subject 
% correct AEM can be calculated in two ways
1. correct AEM / total num of AEM
2. correct AEM / total num of trials
```{r}
#1. % = correct AEM / total num of AEM

#2. % = correct AEM / total num of trials
```

pupil timecourse for 3 trial types (correct, incorrect, no AEM)
```{r}
#1. preswitch

#2. postswitch
```

pupil timecourse for 3 trial types (pupil match, pupil mismatch, no AEM)
```{r}
#1. preswitch

#2. postswitch
```

pupil timecourse for 3 trial types (aem, no AEM)
```{r}
#1. preswitch

#2. postswitch
```

pupil timecourse preswitch
color by babies who made more correct AEMs than incorrect AEMs, and babies who made more incorrect than correct
plot Histogram of the proportion (proportion of correct AEMs)
```{r}
#histogram


#pupil time course

```

pupil timecourse postswitch
color by babies who made more correct AEMs than incorrect AEMs, and babies who made more incorrect than correct
```{r}

```

color = correct vs incorrect AEM
x = time
y = % looking to side
facet wrap = above and below median
also for preswitch vs postswitch
```{r}
#preswitch

#postswitch
```

correlation:
x = % correct (# of correct AEM in preswitch / total number of trials in preswitch)
y = pupil size during 1500-2000ms

get r values
```{r}
#keep 0%


#remove 0%

```

correlation:
x = % correct (# of correct AEM in preswitch / total number of trials in preswitch)
y = pupil size during 2500-4000

get r values
```{r}
#keep 0%


#remove 0%
```

x = percent correct AEM during preswitch
y = percent incorrect AEM during post-switch
```{r}

```

for correct and incorrect AEM, do % of trials per baby for pre vs post
REDO THIS
```{r}
#total num of trials for pre and post
e1 <- ddply(aembreakdown,.(subID,switch),summarise,totaltrials=length(unique(trialnum)))

#type 1 = correct AEM to target, 2 = incorrect AEM to distractor, 3 = no AEM
#correct AEM
e2 <- subset(aembreakdown, type ==1)
e22 <- ddply(e2,.(subID,switch),summarise,totaltrials=length(unique(trialnum)))

newData1 <- data.frame(subID = "1", switch = "2", totaltrials = "0")
newData2 <- data.frame(subID = "2", switch = "1", totaltrials = "0")
newData3 <- data.frame(subID = "2", switch = "2", totaltrials = "0")
newData4 <- data.frame(subID = "5", switch = "1", totaltrials = "0")
newData5 <- data.frame(subID = "6", switch = "2", totaltrials = "0")
newData6 <- data.frame(subID = "7", switch = "2", totaltrials = "0")
newData7 <- data.frame(subID = "8", switch = "1", totaltrials = "0")
newData8 <- data.frame(subID = "8", switch = "2", totaltrials = "0")
newData9 <- data.frame(subID = "9", switch = "2", totaltrials = "0")
newData10 <- data.frame(subID = "10", switch = "2", totaltrials = "0")
newData11 <- data.frame(subID = "11", switch = "1", totaltrials = "0")
newData12 <- data.frame(subID = "12", switch = "2", totaltrials = "0")
newData13 <- data.frame(subID = "13", switch = "1", totaltrials = "0")
newData14 <- data.frame(subID = "14", switch = "2", totaltrials = "0")
newData15 <- data.frame(subID = "17", switch = "1", totaltrials = "0")
newData16 <- data.frame(subID = "17", switch = "2", totaltrials = "0")
newData17 <- data.frame(subID = "21", switch = "1", totaltrials = "0")
newData18 <- data.frame(subID = "21", switch = "2", totaltrials = "0")
newData19 <- data.frame(subID = "25", switch = "2", totaltrials = "0")
newData20 <- data.frame(subID = "26", switch = "2", totaltrials = "0")
newData21 <- data.frame(subID = "28", switch = "2", totaltrials = "0")
newData22 <- data.frame(subID = "31", switch = "2", totaltrials = "0")
newData23 <- data.frame(subID = "33", switch = "2", totaltrials = "0")

e22 <- rbind( e22[1,], newData1, e22[2:29,] )
e22 <- rbind( e22[1:2,], newData2, e22[3:30,] )
e22 <- rbind( e22[1:3,], newData3, e22[4:31,] )
e22 <- rbind( e22[1:4,], newData4, e22[5:32,] )
e22 <- rbind( e22[1:7,], newData5, e22[8:33,] )
e22 <- rbind( e22[1:9,], newData6, e22[10:34,] )
e22 <- rbind( e22[1:10,], newData7, e22[11:35,] )
e22 <- rbind( e22[1:11,], newData8, e22[12:36,] )
e22 <- rbind( e22[1:13,], newData9, e22[14:37,] )
e22 <- rbind( e22[1:15,], newData10, e22[16:38,] )
e22 <- rbind( e22[1:16,], newData11, e22[17:39,] )
e22 <- rbind( e22[1:19,], newData12, e22[20:40,] )
e22 <- rbind( e22[1:20,], newData13, e22[21:41,] )
e22 <- rbind( e22[1:23,], newData14, e22[24:42,] )
e22 <- rbind( e22[1:26,], newData15, e22[27:43,] )
e22 <- rbind( e22[1:27,], newData16, e22[28:44,] )
e22 <- rbind( e22[1:32,], newData17, e22[33:45,] )
e22 <- rbind( e22[1:33,], newData18, e22[34:46,] )
e22 <- rbind( e22[1:39,], newData19, e22[40:47,] )
e22 <- rbind( e22[1:41,], newData20, e22[42:48,] )
e22 <- rbind( e22[1:43,], newData21, e22[44:49,] )
e22 <- rbind( e22[1:45,], newData22, e22[46:50,] )
e22 <- rbind( e22[1:49,], newData23, e22[50:51,] )
e22$totaltrials <- as.numeric(as.character(e22$totaltrials))
e22$subID <- as.numeric(as.character(e22$subID))
e22$switch <- as.numeric(as.character(e22$switch))
e22$percent <- e22$totaltrials / e1$totaltrials

e222 <- ddply(e22,.(switch),summarise,trialavg=mean(percent,na.rm = TRUE),setrials=sd(percent, na.rm = TRUE)/sqrt(length(percent)))
e222$group <- 3

#incorrect AEM
e3 <- subset(aembreakdown, type ==2)
e33 <- ddply(e3,.(subID,switch),summarise,totaltrials=length(unique(trialnum)))

newData1 <- data.frame(subID = "2", switch = "2", totaltrials = "0")
newData2 <- data.frame(subID = "8", switch = "1", totaltrials = "0")
newData3 <- data.frame(subID = "8", switch = "2", totaltrials = "0")
newData4 <- data.frame(subID = "9", switch = "1", totaltrials = "0")
newData5 <- data.frame(subID = "11", switch = "1", totaltrials = "0")
newData6 <- data.frame(subID = "11", switch = "2", totaltrials = "0")
newData7 <- data.frame(subID = "13", switch = "2", totaltrials = "0")
newData8 <- data.frame(subID = "14", switch = "1", totaltrials = "0")
newData9 <- data.frame(subID = "14", switch = "2", totaltrials = "0")
newData10 <- data.frame(subID = "17", switch = "1", totaltrials = "0")
newData11 <- data.frame(subID = "18", switch = "1", totaltrials = "0")
newData12 <- data.frame(subID = "18", switch = "2", totaltrials = "0")
newData13 <- data.frame(subID = "21", switch = "1", totaltrials = "0")
newData14 <- data.frame(subID = "21", switch = "2", totaltrials = "0")
newData15 <- data.frame(subID = "24", switch = "2", totaltrials = "0")
newData16 <- data.frame(subID = "25", switch = "1", totaltrials = "0")
newData17 <- data.frame(subID = "25", switch = "2", totaltrials = "0")
newData18 <- data.frame(subID = "26", switch = "1", totaltrials = "0")
newData19 <- data.frame(subID = "34", switch = "1", totaltrials = "0")
newData20 <- data.frame(subID = "34", switch = "2", totaltrials = "0")

e33 <- rbind( e33[1:3,], newData1, e33[4:32,] )
e33 <- rbind( e33[1:10,], newData2, e33[11:33,] )
e33 <- rbind( e33[1:11,], newData3, e33[12:34,] )
e33 <- rbind( e33[1:12,], newData4, e33[13:35,] )
e33 <- rbind( e33[1:16,], newData5, e33[17:36,] )
e33 <- rbind( e33[1:17,], newData6, e33[18:37,] )
e33 <- rbind( e33[1:21,], newData7, e33[22:38,] )
e33 <- rbind( e33[1:22,], newData8, e33[23:39,] )
e33 <- rbind( e33[1:23,], newData9, e33[24:40,] )
e33 <- rbind( e33[1:26,], newData10, e33[27:41,] )
e33 <- rbind( e33[1:28,], newData11, e33[29:42,] )
e33 <- rbind( e33[1:29,], newData12, e33[30:43,] )
e33 <- rbind( e33[1:32,], newData13, e33[33:44,] )
e33 <- rbind( e33[1:33,], newData14, e33[34:45,] )
e33 <- rbind( e33[1:37,], newData15, e33[38:46,] )
e33 <- rbind( e33[1:38,], newData16, e33[39:47,] )
e33 <- rbind( e33[1:39,], newData17, e33[40:48,] )
e33 <- rbind( e33[1:40,], newData18, e33[41:49,] )
e33 <- rbind( e33[1:50,], newData19)
e33 <- rbind( e33[1:51,], newData20)

e33$totaltrials <- as.numeric(as.character(e33$totaltrials))
e33$subID <- as.numeric(as.character(e33$subID))
e33$switch <- as.numeric(as.character(e33$switch))
e33$percent <- e33$totaltrials / e1$totaltrials

e333 <- ddply(e33,.(switch),summarise,trialavg=mean(percent,na.rm = TRUE),setrials=sd(percent, na.rm = TRUE)/sqrt(length(percent)))
e333$group <- 2
dodge <- position_dodge(width=0.9)
limits <- aes(ymax = trialavg + setrials, ymin=trialavg - setrials)

efinal <- rbind(e222,e333)
ggplot(efinal,aes(x=factor(switch),y=trialavg,fill=factor(group),color=factor(group)))+
  geom_bar(stat="identity",position=dodge)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(y = "% of trials")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0))+
  theme(axis.title = element_text(face="bold", size=16),axis.title.x=element_blank())+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  scale_x_discrete(breaks=c("1","2"),labels=c("pre-switch", "post-switch"))+
  theme(strip.text = element_text(size=16))+
  guides(color=FALSE)+
  scale_color_manual(values = c("#fffcb7", "#bebad9"))+
  scale_fill_manual(values = c("#fffcb7", "#bebad9"),name="Trial breakdown",breaks=c("2","3"),labels=c("incorrect AEMs","correct AEMs"))+
  scale_y_continuous(labels=percent,limits=c(0,.14),breaks=seq(0,.14,.02))+
  theme(legend.position = "top")+
  geom_errorbar(limits, width=0.25,position = position_dodge(0.9),color="black")

#STATS: logistic regression
#code every trial: 1 or 0 for incorrect or correct AEM
zoo <- ddply(orig.sample5,.(subID,switch,TRIAL_INDEX,NEWTRIALNUM),summarise,trialtype=unique(trialtype,na.rm = TRUE))
zoo <- subset(zoo, trialtype < 3)
zoo$trialtype[zoo$trialtype==2] <- 0 #relabel incorrect AEM as 0
zoo$switch[zoo$switch==1] <- 0 #relabelling it for coloring
zoo$switch[zoo$switch==2] <- 1 #relabelling it for coloring

zoo <- within(zoo, {
  subID   <- factor(subID)
  switch <- factor(switch)
  trialtype <- factor(trialtype)
})

model <- glm(trialtype ~ switch,family=binomial(link='logit'),data=zoo)
summary(model)

```

