---
title: "Untitled"
author: "Felicia Zhang"
date: '2018-01-24'
output: html_document
---

```{r setup, include=FALSE}
library(ggplot2) 
library(zoo)
library(reshape)
library(plyr)
library(dplyr)
library(scales) 
library(data.table)
library(signal)
library(matrixStats)
library(lme4)
library(arm)
library(RColorBrewer)
library(lmerTest)
library(boot)

#load preprocessed data
orig.sample2 <- read.csv("/Volumes/emberson/ResearchProjects/Pupillometry/Pinwheels/Data/Pinwheel_Infant_Preprocessed_RemovedOutliers_Nov28.csv")  #Nov28 has bad trials removed
orig.sample2$X <- NULL
orig.sample2$X.1 <- NULL

#recode trial number
orig.sample2$trialnum <- 0
orig.sample2$trialnum[orig.sample2$TRIAL_INDEX == 1 | orig.sample2$TRIAL_INDEX == 9 | orig.sample2$TRIAL_INDEX == 17 | orig.sample2$TRIAL_INDEX == 25 | orig.sample2$TRIAL_INDEX == 33 | orig.sample2$TRIAL_INDEX == 41] <- 1
orig.sample2$trialnum[orig.sample2$TRIAL_INDEX == 2 | orig.sample2$TRIAL_INDEX == 10 | orig.sample2$TRIAL_INDEX == 18 | orig.sample2$TRIAL_INDEX == 26 | orig.sample2$TRIAL_INDEX == 34 | orig.sample2$TRIAL_INDEX == 42] <- 2
orig.sample2$trialnum[orig.sample2$TRIAL_INDEX == 3 | orig.sample2$TRIAL_INDEX == 11 | orig.sample2$TRIAL_INDEX == 19 | orig.sample2$TRIAL_INDEX == 27 | orig.sample2$TRIAL_INDEX == 35 | orig.sample2$TRIAL_INDEX == 43] <- 3
orig.sample2$trialnum[orig.sample2$TRIAL_INDEX == 4 | orig.sample2$TRIAL_INDEX == 12 | orig.sample2$TRIAL_INDEX == 20 | orig.sample2$TRIAL_INDEX == 28 | orig.sample2$TRIAL_INDEX == 36 | orig.sample2$TRIAL_INDEX == 44] <- 4
orig.sample2$trialnum[orig.sample2$TRIAL_INDEX == 5 | orig.sample2$TRIAL_INDEX == 13 | orig.sample2$TRIAL_INDEX == 21 | orig.sample2$TRIAL_INDEX == 29 | orig.sample2$TRIAL_INDEX == 37 | orig.sample2$TRIAL_INDEX == 45] <- 5
orig.sample2$trialnum[orig.sample2$TRIAL_INDEX == 6 | orig.sample2$TRIAL_INDEX == 14 | orig.sample2$TRIAL_INDEX == 22 | orig.sample2$TRIAL_INDEX == 30 | orig.sample2$TRIAL_INDEX == 38 | orig.sample2$TRIAL_INDEX == 46] <- 6
orig.sample2$trialnum[orig.sample2$TRIAL_INDEX == 7 | orig.sample2$TRIAL_INDEX == 15 | orig.sample2$TRIAL_INDEX == 23 | orig.sample2$TRIAL_INDEX == 31 | orig.sample2$TRIAL_INDEX == 39 | orig.sample2$TRIAL_INDEX == 47] <- 7
orig.sample2$trialnum[orig.sample2$TRIAL_INDEX == 8 | orig.sample2$TRIAL_INDEX == 16 | orig.sample2$TRIAL_INDEX == 24 | orig.sample2$TRIAL_INDEX == 32 | orig.sample2$TRIAL_INDEX == 40 | orig.sample2$TRIAL_INDEX == 48] <- 8

#excluded trial 1 of each preswitch sub-block
orig.sample3 <- subset(orig.sample2, !(switch==1 & trialnum==1))

#counting number of babies for criteria 3: contribute at least one trial for 4/6 subblock (2 for preswitch and 2 for postswitch)
#exclude: 3, 4, 16, 19, 22, 27, 29, 30 (8 subs excluded)
orig.sample4 <- subset(orig.sample3, subID != 3)
orig.sample4 <- subset(orig.sample4, subID != 4)
orig.sample4 <- subset(orig.sample4, subID != 16)
orig.sample4 <- subset(orig.sample4, subID != 19)
orig.sample4 <- subset(orig.sample4, subID != 22)
orig.sample4 <- subset(orig.sample4, subID != 27)
orig.sample4 <- subset(orig.sample4, subID != 29)
orig.sample4 <- subset(orig.sample4, subID != 30)

#orig.sample2 = trials with more than 50% looking
#orig.sample3 = excluded trial 1 of each preswitch sub-block
#orig.sample4 = excluded subjects
```

AEM coding
```{r}
poo <- orig.sample4

#1. Binning every 100ms, to make sure that it's actually a fixation for lookstotarget
moo <- data.frame(subID=numeric(),trialnum=numeric(),timecode=numeric(),block=numeric(),switch=numeric(),lookingattarget=numeric())
subs <- unique(poo$subID)
time <- seq(100,4000, by=100) #the time bins we are trying to create (0-4000ms) doing 4000ms 

for (j in 1:length(subs)) {
  #gets every trial for 1 subject
  trials <- unique(poo$TRIAL_INDEX[poo$subID==subs[j]])
  print(j)
  for (i in 1:length(trials)) {
    #gets all sample for 1 trial  
    woo <- subset(poo, subID==subs[j] & TRIAL_INDEX == trials[i])
    c <- woo$block[1]
    cc <- woo$switch[1]
    ccc <- woo$trialnum[1]
    for (k in 1:length(time)){
      #for every 25 sample/100 ms, get lookattarget column
      if (k==1) {
        target <- woo$lookattarget[woo$TIMECODE < time[k]+1] #gets 0-100ms
        d <- unique(target)
        dd <- which(d==1)
      } else {
        target <- woo$lookattarget[woo$TIMECODE < time[k]+1 & woo$TIMECODE > time[k-1]-1]
        d <- unique(target)
        dd <- which(d==1)
      }
      #see if entire chunk is looking at target
      if (length(target)==0) { #no samples collected during this time
        aa <- c(subs[j],trials[i],ccc,c,cc,time[k],99)   
        moo <- rbind(moo,aa)
        warnings()
      } else if (length(d)==1 & d==1) { #looking at target entire time
        aa <- c(subs[j],trials[i],ccc,c,cc,time[k],d)   
        moo <- rbind(moo,aa)
        warnings()
      } else if (length(d)==1 & d==0) { #looking at distractor entire time
        aa <- c(subs[j],trials[i],ccc,c,cc,time[k],d)   
        moo <- rbind(moo,aa)
        warnings()
      } else if (length(d)==1 & d==5) { #looking at center entire time
        aa <- c(subs[j],trials[i],ccc,c,cc,time[k],d)   
        moo <- rbind(moo,aa)
        warnings()
      } else if (length(d) > 1 & length(dd) < 1) { #not looking at same location and not looking at target (looking at distractor and center)
        aa <- c(subs[j],trials[i],ccc,c,cc,time[k],9)   
        moo <- rbind(moo,aa) 
        warnings()
      } else { #not looking at same location and but looking at target sometimes
        #calculate proportion looking  
        b <- length(which(target==1)) #samples where subs are looking at target
        bb <- length(which(target==1))/length(target) #looking at target/25
        aa <- c(subs[j],trials[i],ccc,c,cc,time[k],bb) 
        moo <- rbind(moo,aa)
        warnings()
      }}}}

names(moo)[1] <- "subID"
names(moo)[2] <- "trialnum"
names(moo)[3] <- "trialnum2"
names(moo)[4] <- "block"
names(moo)[5] <- "switch"
names(moo)[6] <- "timecode"
names(moo)[7] <- "lookattarget"

#0 = distractor, 1 = target, 5 = center, 9 = looking at distractor and center, 99 = no data collected
x1 <- subset(moo, lookattarget < 99) #remove no data collected
x1$looktocenter <- 0

#coding which trials looked to center before making AEM
subs <- unique(x1$subID)
for (j in 1:length(subs)) {
  #gets every trial for 1 subject
  trials <- unique(x1$trialnum[x1$subID==subs[j]])
  print(j)
  for (i in 1:length(trials)) {
    foo <- subset(x1, subID==subs[j] & trialnum==trials[i] & timecode < 701)  
    if (any(foo$lookattarget==5)) {
      x1$looktocenter[x1$subID==subs[j] & x1$trialnum==trials[i]] <- 1
    }
  }}

#code trial type: pupil match, pupil mismatch, or no AEM 
#must look to center first, must make eye movement in 700-2700ms
#type 1 = pupil match, 2 = pupil mismatch, 3 = no AEM

x1$type <- 3
subs <- unique(x1$subID)

for (j in 1:length(subs)) {
  #gets every trial for 1 subject
  trials <- unique(x1$trialnum[x1$subID==subs[j]])
  print(j)
  for (i in 1:length(trials)) {
    #current trial
    foo <- subset(x1, subID==subs[j] & trialnum==trials[i] & timecode > 699 & timecode <2601) 
    if (any(foo$lookattarget==0) & foo$looktocenter[1]==1) {
      x1$type[x1$subID==subs[j] & x1$trialnum==trials[i]] <- 2
    }
    if (any(foo$lookattarget==1) & foo$looktocenter[1]==1) {
      x1$type[x1$subID==subs[j] & x1$trialnum==trials[i]] <- 1
    }
    }
  }

pupilbreakdown <- x1
```

RT using minimum
group correct and incorrect AEMs together
0 = distractor, 1 = target, 5 = center, 9 = looking at distractor and center, 99 = no data collected
```{r}
looks <- subset(pupilbreakdown, lookattarget ==0 | lookattarget ==1) #only keep distractor and target

#if AEM is anything from 700-2700ms, then RT is everything ater 2700
look2 <- subset(looks, timecode > 2600)

#now for every trial get the minimum time, when babies FIRST LOOKED
coo <- ddply(look2,.(subID, trialnum,trialnum2,block,switch,looktocenter,type ),summarise,time=min(timecode,na.rm = TRUE))
coo2 <- ddply(coo,.(trialnum2,switch),summarise,meantime=mean(time,na.rm = TRUE),setime=sd(time, na.rm = TRUE)/sqrt(length(time)))
coo2$meantime2 <- coo2$meantime-2550

ggplot(coo2,aes(x=trialnum2,y=meantime2,color=factor(switch),fill=factor(switch)))+
  geom_line()+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("When babies look to side (correct + incorrect)")+
  labs(x = "Trial number", y = "Time after target appears (ms)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  geom_ribbon(aes(ymin=meantime2-setime,ymax=meantime2+setime),alpha=0.4)+
  scale_x_continuous(limits=c(1,8),breaks=seq(1,8,1))+
  scale_y_continuous(limits=c(400,800),breaks=seq(400,800,50))+
  guides(color=FALSE)+
  scale_fill_brewer(palette="Set1",name="Switch",breaks=c("1","2"),labels=c("Pre-switch", "Post-switch"))+
  scale_color_brewer(palette="Set1")+
  theme(legend.position = "top")+
  theme(plot.title = element_text(hjust = 0.5))

#correlation
cor.test(coo2$trialnum2[coo2$switch==1], coo2$meantime2[coo2$switch==1], alternative = "two.sided", method = "pearson")
#preswitch is not p = 0.2, r = -0.54
cor.test(coo2$trialnum2[coo2$switch==2], coo2$meantime2[coo2$switch==2], alternative = "two.sided", method = "pearson")
#postswitch is significant p = 0.3, r = -0.41

#combine pre-switch and post switch
coo3 <- ddply(coo,.(trialnum2),summarise,meantime=mean(time,na.rm = TRUE),setime=sd(time, na.rm = TRUE)/sqrt(length(time)))
coo3$meantime2 <- coo3$meantime-2550

ggplot(coo3,aes(x=trialnum2,y=meantime2))+
  geom_line()+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("When babies look to side (correct + incorrect)")+
  labs(x = "Trial number", y = "Time after target appears (ms)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  geom_ribbon(aes(ymin=meantime2-setime,ymax=meantime2+setime),alpha=0.4)+
  scale_x_continuous(limits=c(1,8),breaks=seq(1,8,1))+
  scale_y_continuous(limits=c(400,800),breaks=seq(400,800,50))+
  theme(legend.position = "top")+
  theme(plot.title = element_text(hjust = 0.5))

#correlation
cor.test(coo3$trialnum2, coo3$meantime2, alternative = "two.sided", method = "pearson")
#almost sig p = 0.21, r = -0.5
```

How to deal with AEM trials?
1. removing AEM trials completely
2. negative RTs, 
Also plot distribution for both
```{r}
#remove AEM trials 

#type 1 = pupil match, 2 = pupil mismatch, 3 = no AEM

pupilbreakdown2 <- subset(pupilbreakdown, type > 1)
#only keep distractor and target
looks <- subset(pupilbreakdown2, lookattarget ==0 | lookattarget ==1) 

#if AEM is anything from 700-2700ms, then RT is everything ater 2700
look2 <- subset(looks, timecode > 2600)

#now for every trial get the minimum time, when babies FIRST LOOKED
coo <- ddply(look2,.(subID, trialnum,trialnum2,block,switch,looktocenter,type ),summarise,time=min(timecode,na.rm = TRUE))
coo2 <- ddply(coo,.(trialnum2,switch),summarise,meantime=mean(time,na.rm = TRUE),setime=sd(time, na.rm = TRUE)/sqrt(length(time)))
coo2$meantime2 <- coo2$meantime-2550

ggplot(coo2,aes(x=trialnum2,y=meantime2,color=factor(switch),fill=factor(switch)))+
  geom_line()+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("When babies look to side (correct + incorrect)")+
  labs(x = "Trial number", y = "Time after target appears (ms)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  geom_ribbon(aes(ymin=meantime2-setime,ymax=meantime2+setime),alpha=0.4)+
  scale_x_continuous(limits=c(1,8),breaks=seq(1,8,1))+
  scale_y_continuous(limits=c(400,800),breaks=seq(400,800,50))+
  guides(color=FALSE)+
  scale_fill_brewer(palette="Set1",name="Switch",breaks=c("1","2"),labels=c("Pre-switch", "Post-switch"))+
  scale_color_brewer(palette="Set1")+
  theme(legend.position = "top")+
  theme(plot.title = element_text(hjust = 0.5))

#correlation
cor.test(coo2$trialnum2[coo2$switch==1], coo2$meantime2[coo2$switch==1], alternative = "two.sided", method = "pearson")
#preswitch is not p = 0.17, r = -0.58
cor.test(coo2$trialnum2[coo2$switch==2], coo2$meantime2[coo2$switch==2], alternative = "two.sided", method = "pearson")
#postswitch is significant p = 0.35, r = -0.38
```

How to deal with AEM trials?
1. removing AEM trials completely
2. negative RTs, 
Also plot distribution for both
```{r}
#negative RTs
#only keep distractor and target
looks <- subset(pupilbreakdown2, lookattarget ==0 | lookattarget ==1) 
looks2 <- subset(looks,looktocenter==1 )
#now for every trial get the minimum time, when babies FIRST LOOKED
coo <- ddply(looks,.(subID, trialnum,trialnum2,block,switch,looktocenter,type ),summarise,time=min(timecode,na.rm = TRUE))
coo2 <- ddply(coo,.(trialnum2,switch),summarise,meantime=mean(time,na.rm = TRUE),setime=sd(time, na.rm = TRUE)/sqrt(length(time)))
coo2$meantime2 <- coo2$meantime-2550

ggplot(coo2,aes(x=trialnum2,y=meantime2,color=factor(switch),fill=factor(switch)))+
  geom_line()+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("When babies look to side (correct + incorrect)")+
  labs(x = "Trial number", y = "Time after target appears (ms)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  geom_ribbon(aes(ymin=meantime2-setime,ymax=meantime2+setime),alpha=0.4)+
  scale_x_continuous(limits=c(1,8),breaks=seq(1,8,1))+
  scale_y_continuous(limits=c(400,800),breaks=seq(400,800,50))+
  guides(color=FALSE)+
  scale_fill_brewer(palette="Set1",name="Switch",breaks=c("1","2"),labels=c("Pre-switch", "Post-switch"))+
  scale_color_brewer(palette="Set1")+
  theme(legend.position = "top")+
  theme(plot.title = element_text(hjust = 0.5))

#correlation
cor.test(coo2$trialnum2[coo2$switch==1], coo2$meantime2[coo2$switch==1], alternative = "two.sided", method = "pearson")
#preswitch is not p = 0.26, r = -0.48
cor.test(coo2$trialnum2[coo2$switch==2], coo2$meantime2[coo2$switch==2], alternative = "two.sided", method = "pearson")
#postswitch is significant p = 0.04, r = -0.73
```


RT
only correct 
0 = distractor, 1 = target, 5 = center, 9 = looking at distractor and center, 99 = no data collected
```{r}
looks.correct <- subset(pupilbreakdown, lookattarget ==1) #only keep target

#if AEM is anything from 700-2700ms, then RT is everything ater 2700
looks.correct2 <- subset(looks.correct, timecode > 2600)

#now for every trial get the minimum time 
hoo <- ddply(looks.correct2,.(subID, trialnum,trialnum2,block,switch,lookattarget,looktocenter,type ),summarise,time=min(timecode,na.rm = TRUE))
hoo2 <- ddply(hoo,.(trialnum2,switch),summarise,meantime=mean(time,na.rm = TRUE),setime=sd(time, na.rm = TRUE)/sqrt(length(time)))
hoo2$meantime2 <- hoo2$meantime-2550

ggplot(hoo2,aes(x=trialnum2,y=meantime2,color=factor(switch),fill=factor(switch)))+
  geom_line()+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("When babies look to side (correct)")+
  labs(x = "Trial number", y = "Time after target appears (ms)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  geom_ribbon(aes(ymin=meantime2-setime,ymax=meantime2+setime),alpha=0.4)+
  scale_x_continuous(limits=c(1,8),breaks=seq(1,8,1))+
  scale_y_continuous(limits=c(400,800),breaks=seq(400,800,50))+
  guides(color=FALSE)+
  scale_fill_brewer(palette="Set1",name="Switch",breaks=c("1","2"),labels=c("Pre-switch", "Post-switch"))+
  scale_color_brewer(palette="Set1")+
  theme(legend.position = "top")+
  theme(plot.title = element_text(hjust = 0.5))

#correlation
cor.test(hoo2$trialnum2[hoo2$switch==1], hoo2$meantime2[hoo2$switch==1], alternative = "two.sided", method = "pearson")
#preswitch is not, p = 0.37 r = -0.39
cor.test(hoo2$trialnum2[hoo2$switch==2], hoo2$meantime2[hoo2$switch==2], alternative = "two.sided", method = "pearson")
#postswitch is almost significant p = 0.08 r = -0.64

#combine pre-switch and post switch
hoo3 <- ddply(hoo,.(trialnum2),summarise,meantime=mean(time,na.rm = TRUE),setime=sd(time, na.rm = TRUE)/sqrt(length(time)))
hoo3$meantime2 <- hoo3$meantime-2550

ggplot(hoo3,aes(x=trialnum2,y=meantime2))+
  geom_line()+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("When babies look to side (correct)")+
  labs(x = "Trial number", y = "Time after target appears (ms)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  geom_ribbon(aes(ymin=meantime2-setime,ymax=meantime2+setime),alpha=0.4)+
  scale_x_continuous(limits=c(1,8),breaks=seq(1,8,1))+
  scale_y_continuous(limits=c(400,800),breaks=seq(400,800,50))+
  theme(legend.position = "top")+
  theme(plot.title = element_text(hjust = 0.5))

#correlation
cor.test(hoo3$trialnum2, hoo3$meantime2, alternative = "two.sided", method = "pearson")
#almost sig p = 0.06, r = -0.68
```





