---
title: "Untitled"
author: "Felicia Zhang"
date: '2018-01-24'
output: html_document
---

```{r setup, include=FALSE}
library(ggplot2) 
library(zoo)
library(reshape)
library(plyr)
library(scales) 
library(data.table)
library(signal)
library(matrixStats)
library(lme4)
library(arm)
library(RColorBrewer)
library(lmerTest)
library(boot)

#load preprocessed data
#Oct21 has PUPIL_CORRECTED_2 calculated using 0-1500ms
orig.sample <- read.csv("/Volumes/emberson/ResearchProjects/Pupillometry/Pinwheels/Data/Pinwheel_Infant_Preprocessed_AllSamples_Nov28.csv") #Nov28 has trackloss % for all trials
orig.sample2 <- read.csv("/Volumes/emberson/ResearchProjects/Pupillometry/Pinwheels/Data/Pinwheel_Infant_Preprocessed_RemovedOutliers_Nov28.csv")  #Nov28 has bad trials removed
orig.sample$X <- NULL
orig.sample2$X <- NULL
orig.sample$X.1 <- NULL
orig.sample2$X.1 <- NULL

#REMOVE TRIALS 5-8 FOR EACH SUBBLOCK
orig.sample$trialnum <- 0
orig.sample$trialnum[orig.sample$TRIAL_INDEX == 1 | orig.sample$TRIAL_INDEX == 9 | orig.sample$TRIAL_INDEX == 17 | orig.sample$TRIAL_INDEX == 25 | orig.sample$TRIAL_INDEX == 33 | orig.sample$TRIAL_INDEX == 41] <- 1
orig.sample$trialnum[orig.sample$TRIAL_INDEX == 2 | orig.sample$TRIAL_INDEX == 10 | orig.sample$TRIAL_INDEX == 18 | orig.sample$TRIAL_INDEX == 26 | orig.sample$TRIAL_INDEX == 34 | orig.sample$TRIAL_INDEX == 42] <- 2
orig.sample$trialnum[orig.sample$TRIAL_INDEX == 3 | orig.sample$TRIAL_INDEX == 11 | orig.sample$TRIAL_INDEX == 19 | orig.sample$TRIAL_INDEX == 27 | orig.sample$TRIAL_INDEX == 35 | orig.sample$TRIAL_INDEX == 43] <- 3
orig.sample$trialnum[orig.sample$TRIAL_INDEX == 4 | orig.sample$TRIAL_INDEX == 12 | orig.sample$TRIAL_INDEX == 20 | orig.sample$TRIAL_INDEX == 28 | orig.sample$TRIAL_INDEX == 36 | orig.sample$TRIAL_INDEX == 44] <- 4
orig.sample$trialnum[orig.sample$TRIAL_INDEX == 5 | orig.sample$TRIAL_INDEX == 13 | orig.sample$TRIAL_INDEX == 21 | orig.sample$TRIAL_INDEX == 29 | orig.sample$TRIAL_INDEX == 37 | orig.sample$TRIAL_INDEX == 45] <- 5
orig.sample$trialnum[orig.sample$TRIAL_INDEX == 6 | orig.sample$TRIAL_INDEX == 14 | orig.sample$TRIAL_INDEX == 22 | orig.sample$TRIAL_INDEX == 30 | orig.sample$TRIAL_INDEX == 38 | orig.sample$TRIAL_INDEX == 46] <- 6
orig.sample$trialnum[orig.sample$TRIAL_INDEX == 7 | orig.sample$TRIAL_INDEX == 15 | orig.sample$TRIAL_INDEX == 23 | orig.sample$TRIAL_INDEX == 31 | orig.sample$TRIAL_INDEX == 39 | orig.sample$TRIAL_INDEX == 47] <- 7
orig.sample$trialnum[orig.sample$TRIAL_INDEX == 8 | orig.sample$TRIAL_INDEX == 16 | orig.sample$TRIAL_INDEX == 24 | orig.sample$TRIAL_INDEX == 32 | orig.sample$TRIAL_INDEX == 40 | orig.sample$TRIAL_INDEX == 48] <- 8

orig.sample2$trialnum <- 0
orig.sample2$trialnum[orig.sample2$TRIAL_INDEX == 1 | orig.sample2$TRIAL_INDEX == 9 | orig.sample2$TRIAL_INDEX == 17 | orig.sample2$TRIAL_INDEX == 25 | orig.sample2$TRIAL_INDEX == 33 | orig.sample2$TRIAL_INDEX == 41] <- 1
orig.sample2$trialnum[orig.sample2$TRIAL_INDEX == 2 | orig.sample2$TRIAL_INDEX == 10 | orig.sample2$TRIAL_INDEX == 18 | orig.sample2$TRIAL_INDEX == 26 | orig.sample2$TRIAL_INDEX == 34 | orig.sample2$TRIAL_INDEX == 42] <- 2
orig.sample2$trialnum[orig.sample2$TRIAL_INDEX == 3 | orig.sample2$TRIAL_INDEX == 11 | orig.sample2$TRIAL_INDEX == 19 | orig.sample2$TRIAL_INDEX == 27 | orig.sample2$TRIAL_INDEX == 35 | orig.sample2$TRIAL_INDEX == 43] <- 3
orig.sample2$trialnum[orig.sample2$TRIAL_INDEX == 4 | orig.sample2$TRIAL_INDEX == 12 | orig.sample2$TRIAL_INDEX == 20 | orig.sample2$TRIAL_INDEX == 28 | orig.sample2$TRIAL_INDEX == 36 | orig.sample2$TRIAL_INDEX == 44] <- 4
orig.sample2$trialnum[orig.sample2$TRIAL_INDEX == 5 | orig.sample2$TRIAL_INDEX == 13 | orig.sample2$TRIAL_INDEX == 21 | orig.sample2$TRIAL_INDEX == 29 | orig.sample2$TRIAL_INDEX == 37 | orig.sample2$TRIAL_INDEX == 45] <- 5
orig.sample2$trialnum[orig.sample2$TRIAL_INDEX == 6 | orig.sample2$TRIAL_INDEX == 14 | orig.sample2$TRIAL_INDEX == 22 | orig.sample2$TRIAL_INDEX == 30 | orig.sample2$TRIAL_INDEX == 38 | orig.sample2$TRIAL_INDEX == 46] <- 6
orig.sample2$trialnum[orig.sample2$TRIAL_INDEX == 7 | orig.sample2$TRIAL_INDEX == 15 | orig.sample2$TRIAL_INDEX == 23 | orig.sample2$TRIAL_INDEX == 31 | orig.sample2$TRIAL_INDEX == 39 | orig.sample2$TRIAL_INDEX == 47] <- 7
orig.sample2$trialnum[orig.sample2$TRIAL_INDEX == 8 | orig.sample2$TRIAL_INDEX == 16 | orig.sample2$TRIAL_INDEX == 24 | orig.sample2$TRIAL_INDEX == 32 | orig.sample2$TRIAL_INDEX == 40 | orig.sample2$TRIAL_INDEX == 48] <- 8

orig.sample3 <- subset(orig.sample2, trialnum > 1)

#orig.sample = all trials
#orig.sample2 = trials with more than 50% looking
#orig.sample3 = remove trial 1 of each sublock
```

Change from previous data analysis: remove trial 1 of each sublock

AEM coding
```{r}
poo <- orig.sample3

#1. Binning every 100ms, to make sure that it's actually a fixation for lookstotarget
moo <- data.frame(subID=numeric(),trialnum=numeric(),timecode=numeric(),lookingattarget=numeric())
subs <- unique(poo$subID)
time <- seq(100,4000, by=100) #the time bins we are trying to create (0-4000ms) doing 4000ms bc s

for (j in 1:length(subs)) {
  #gets every trial for 1 subject
  trials <- unique(poo$TRIAL_INDEX[poo$subID==subs[j]])
  print(j)
  for (i in 1:length(trials)) {
    #gets all sample for 1 trial  
    woo <- subset(poo, subID==subs[j] & TRIAL_INDEX == trials[i])
    c <- woo$block[1]
    for (k in 1:length(time)){
      #for every 25 sample/100 ms, get lookattarget column
      if (k==1) {
        target <- woo$lookattarget[woo$TIMECODE < time[k]+1] #gets 0-100ms
        d <- unique(target)
        dd <- which(d==1)
      } else {
        target <- woo$lookattarget[woo$TIMECODE < time[k]+1 & woo$TIMECODE > time[k-1]-1]
        d <- unique(target)
        dd <- which(d==1)
      }
      #see if entire chunk is looking at target
      if (length(target)==0) { #no samples collected during this time
        aa <- c(subs[j],trials[i],c,time[k],99)   
        moo <- rbind(moo,aa)
        warnings()
      } else if (length(d)==1 & d==1) { #looking at target entire time
        aa <- c(subs[j],trials[i],c,time[k],d)   
        moo <- rbind(moo,aa)
        warnings()
      } else if (length(d)==1 & d==0) { #looking at distractor entire time
        aa <- c(subs[j],trials[i],c,time[k],d)   
        moo <- rbind(moo,aa)
        warnings()
      } else if (length(d)==1 & d==5) { #looking at center entire time
        aa <- c(subs[j],trials[i],c,time[k],d)   
        moo <- rbind(moo,aa)
        warnings()
      } else if (length(d) > 1 & length(dd) < 1) { #not looking at same location and not looking at target (looking at distractor and center)
        aa <- c(subs[j],trials[i],c,time[k],9)   
        moo <- rbind(moo,aa) 
        warnings()
      } else { #not looking at same location and but looking at target sometimes
        #calculate proportion looking  
        b <- length(which(target==1)) #samples where subs are looking at target
        bb <- length(which(target==1))/length(target) #looking at target/25
        aa <- c(subs[j],trials[i],c,time[k],bb) 
        moo <- rbind(moo,aa)
        warnings()
      }}}}

names(moo)[1] <- "subID"
names(moo)[2] <- "trialnum"
names(moo)[3] <- "block"
names(moo)[4] <- "timecode"
names(moo)[5] <- "lookattarget"

moo$switch <- 1
moo$switch[moo$trialnum > 8 & moo$trialnum < 17 ] <- 2
moo$switch[moo$trialnum > 24 & moo$trialnum < 33 ] <- 2
moo$switch[moo$trialnum > 40 ] <- 2

#0 = distractor, 1 = target, 5 = center, 9 = looking at distractor and center, 99 = no data collected
x1 <- subset(moo, lookattarget < 99) #remove no data collected
x1$looktocenter <- 0

#coding which trials looked to center before making AEM
subs <- unique(x1$subID)
for (j in 1:length(subs)) {
  #gets every trial for 1 subject
  trials <- unique(x1$trialnum[x1$subID==subs[j]])
  print(j)
  for (i in 1:length(trials)) {
    foo <- subset(x1, subID==subs[j] & trialnum==trials[i] & timecode < 701)  
    if (any(foo$lookattarget==5)) {
      x1$looktocenter[x1$subID==subs[j] & x1$trialnum==trials[i]] <- 1
    }
  }}

#code trial type: correct AEM, incorrect AEM, or no AEM 
#must look to center first, must make eye movement in 700-2700ms
#type 1 = correct AEM to target, 2 = incorrect AEM to distractor, 3 = no AEM

x1$type <- 3
subs <- unique(x1$subID)
for (j in 1:length(subs)) {
  #gets every trial for 1 subject
  trials <- unique(x1$trialnum[x1$subID==subs[j]])
  print(j)
  for (i in 1:length(trials)) {
    foo <- subset(x1, subID==subs[j] & trialnum==trials[i] & timecode > 699 & timecode <2601) #2600=2600-2699
    if (any(foo$lookattarget==0) & foo$looktocenter[1]==1) {
      x1$type[x1$subID==subs[j] & x1$trialnum==trials[i]] <- 2
    }
    if (any(foo$lookattarget==1) & foo$looktocenter[1]==1) {
      x1$type[x1$subID==subs[j] & x1$trialnum==trials[i]] <- 1
    }}}

x1$trialnum2 <- 0
x1$trialnum2[x1$trialnum == 1 | x1$trialnum == 9 | x1$trialnum == 17 | x1$trialnum == 25 | x1$trialnum == 33 | x1$trialnum == 41] <- 1
x1$trialnum2[x1$trialnum == 2 | x1$trialnum == 10 | x1$trialnum == 18 | x1$trialnum == 26 | x1$trialnum == 34 | x1$trialnum == 42] <- 2
x1$trialnum2[x1$trialnum == 3 | x1$trialnum == 11 | x1$trialnum == 19 | x1$trialnum == 27 | x1$trialnum == 35 | x1$trialnum == 43] <- 3
x1$trialnum2[x1$trialnum == 4 | x1$trialnum == 12 | x1$trialnum == 20 | x1$trialnum == 28 | x1$trialnum == 36 | x1$trialnum == 44] <- 4
x1$trialnum2[x1$trialnum == 5 | x1$trialnum == 13 | x1$trialnum == 21 | x1$trialnum == 29 | x1$trialnum == 37 | x1$trialnum == 45] <- 5
x1$trialnum2[x1$trialnum == 6 | x1$trialnum == 14 | x1$trialnum == 22 | x1$trialnum == 30 | x1$trialnum == 38 | x1$trialnum == 46] <- 6
x1$trialnum2[x1$trialnum == 7 | x1$trialnum == 15 | x1$trialnum == 23 | x1$trialnum == 31 | x1$trialnum == 39 | x1$trialnum == 47] <- 7
x1$trialnum2[x1$trialnum == 8 | x1$trialnum == 16 | x1$trialnum == 24 | x1$trialnum == 32 | x1$trialnum == 40 | x1$trialnum == 48] <- 8

aembreakdown <- x1
```

number of trials completed per subject
```{r}
v1 <- ddply(orig.sample3,.(subID),summarise,trials=length(unique(TRIAL_INDEX,na.rm = TRUE)))  
v1$group <- 1
names(v1)[2] <- "aem"

ggplot(v1,aes(x=factor(subID),y=aem))+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat="identity")+
  ggtitle("Number of trials included per subject (max = 42)")+
  labs(x = "Subject ID", y = "Number of trials")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  scale_y_continuous(limits=c(0,42),breaks=seq(0,42,2))

v1$percent <- v1$aem/42
ggplot(v1,aes(x=factor(subID),y=percent))+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat="identity")+ggtitle("Percent of trials included per subject (max = 42)")+
  labs(x = "Subject ID", y = "% of trials")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,.1))
```

number of trials broken down by block and switch
```{r}
a1 <- ddply(orig.sample3,.(subID,block,switch),summarise,trials=length(unique(TRIAL_INDEX,na.rm = TRUE)))  
a2 <- ddply(a1,.(block,switch),summarise,trials=sum(trials,na.rm = TRUE))
dodge <- position_dodge(width=0.9)
split <- c(`1` = "block 1",`2` = "block 2",`3` = "block 3")

ggplot(a2,aes(x=factor(switch),y=trials,fill=factor(switch),color=factor(switch)))+
  geom_bar(stat="identity",position=dodge)+
  labs(y = "Number of trials")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20),axis.title.x=element_blank())+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  guides(color=FALSE)+facet_wrap(~block,labeller = as_labeller(split))+
  theme(strip.text = element_text(size=16))+
  scale_x_discrete(breaks=c("1","2"),labels=c("pre-switch", "post-switch"))+
  scale_y_continuous(limits=c(0,200),breaks=seq(0,200,25))+guides(fill=FALSE)
```

number of babies broken down by block and switch
```{r}
b1 <- ddply(orig.sample3,.(block,switch),summarise,numsubjects=length(unique(subID,na.rm = TRUE)))  
dodge <- position_dodge(width=0.9)
split <- c(`1` = "block 1",`2` = "block 2",`3` = "block 3")

ggplot(b1,aes(x=factor(switch),y=numsubjects,fill=factor(switch),color=factor(switch)))+
  geom_bar(stat="identity",position=dodge)+
  labs(y = "Number of babies")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20),axis.title.x=element_blank())+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  guides(color=FALSE)+facet_wrap(~block,labeller = as_labeller(split))+
  theme(strip.text = element_text(size=16))+
  scale_x_discrete(breaks=c("1","2"),labels=c("pre-switch", "post-switch"))+
  scale_y_continuous(limits=c(0,34),breaks=seq(0,34,2))+guides(fill=FALSE)
```

AEM break down by number and percentage for each subject
```{r}
z1 <- ddply(orig.sample3,.(subID),summarise,trials=length(unique(TRIAL_INDEX,na.rm = TRUE)))  
z1$group <- 1
names(z1)[2] <- "numoftrials"

#breaking it down for correct and incorrect
#type 1 = correct AEM to target, 2 = incorrect AEM to distractor, 3 = no AEM
z2 <- ddply(aembreakdown,.(subID,type),summarise,numoftrials=length(unique(trialnum,na.rm = TRUE)))  
z2 <- subset(z2, type < 3) #only want correct and incorrect
z3 <- subset(z2, type==1)
z3$type <- NULL
z3$group <- 3

newData1 <- data.frame(subID = "2", numoftrials = "0", group = "3")
newData2 <- data.frame(subID = "7", numoftrials = "0", group = "3")
newData3 <- data.frame(subID = "8", numoftrials = "0", group = "3")
newData4 <- data.frame(subID = "17", numoftrials = "0", group = "3")
newData5 <- data.frame(subID = "19", numoftrials = "0", group = "3")
newData6 <- data.frame(subID = "21", numoftrials = "0", group = "3")
newData7 <- data.frame(subID = "22", numoftrials = "0", group = "3")
newData8 <- data.frame(subID = "27", numoftrials = "0", group = "3")
newData9 <- data.frame(subID = "31", numoftrials = "0", group = "3")

z3 <- rbind( z3[1,], newData1, z3[2:25,] )
z3 <- rbind( z3[1:6,], newData2, z3[7:26,] )
z3 <- rbind( z3[1:7,], newData3, z3[8:27,] )
z3 <- rbind( z3[1:16,], newData4, z3[17:28,] )
z3 <- rbind( z3[1:18,], newData5, z3[19:29,] )
z3 <- rbind( z3[1:20,], newData6, z3[21:30,] )
z3 <- rbind( z3[1:21,], newData7, z3[22:31,] )
z3 <- rbind( z3[1:26,], newData8, z3[27:32,] )
z3 <- rbind( z3[1:30,], newData9, z3[31:33,] )
z3$numoftrials <- as.numeric(as.character(z3$numoftrials))
z3$subID <- as.numeric(as.character(z3$subID))

z4 <- subset(z2, type==2)
z4$type <- NULL
z4$group <- 2

newData1 <- data.frame(subID = "3", numoftrials = "0", group = "2")
newData2 <- data.frame(subID = "8", numoftrials = "0", group = "2")
newData3 <- data.frame(subID = "11", numoftrials = "0", group = "2")
newData4 <- data.frame(subID = "14", numoftrials = "0", group = "2")
newData5 <- data.frame(subID = "18", numoftrials = "0", group = "2")
newData6 <- data.frame(subID = "19", numoftrials = "0", group = "2")
newData7 <- data.frame(subID = "21", numoftrials = "0", group = "2")
newData8 <- data.frame(subID = "22", numoftrials = "0", group = "2")
newData9 <- data.frame(subID = "25", numoftrials = "0", group = "2")
newData10 <- data.frame(subID = "30", numoftrials = "0", group = "2")
newData11 <- data.frame(subID = "34", numoftrials = "0", group = "2")

z4 <- rbind( z4[1:2,], newData1, z4[3:23,] )
z4 <- rbind( z4[1:7,], newData2, z4[8:24,] )
z4 <- rbind( z4[1:10,], newData3, z4[11:25,] )
z4 <- rbind( z4[1:13,], newData4, z4[14:26,] )
z4 <- rbind( z4[1:17,], newData5, z4[18:27,] )
z4 <- rbind( z4[1:18,], newData6, z4[19:28,] )
z4 <- rbind( z4[1:20,], newData7, z4[21:29,] )
z4 <- rbind( z4[1:21,], newData8, z4[22:30,] )
z4 <- rbind( z4[1:24,], newData9, z4[25:31,] )
z4 <- rbind( z4[1:29,], newData10, z4[30:32,] )
z4 <- rbind( z4[1:33,], newData11)
z4$numoftrials <- as.numeric(as.character(z4$numoftrials))
z4$subID <- as.numeric(as.character(z4$subID))

#group 1 = all trials, group 2 = incorrect, group 3= correct
z1$numoftrials <- z1$numoftrials - z4$numoftrials - z3$numoftrials

zfinal <- rbind(z1,z4,z3)
sort(zfinal$subID)
ggplot(zfinal,aes(x=factor(subID),y=numoftrials,color=factor(group),fill=factor(group)))+
  geom_bar(stat="identity")+
  labs(x = "Subject", y = "Number of trials")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  guides(color=FALSE)+
  scale_fill_brewer(palette="Set3",name="Trial breakdown",breaks=c("1","2","3"),labels=c("no AEM", "incorrect AEMs","correct AEMs"))+
  scale_color_brewer(palette="Set3")+
  scale_y_continuous(limits=c(0,48),breaks=seq(0,48,4))+
  theme(legend.position = "bottom")

#percent
zfinal$percent <- 0

for (j in 1:length(subs)) {
 t <- sum(zfinal$numoftrials[zfinal$subID==subs[j]])
 zfinal$percent[zfinal$subID==subs[j]] <- zfinal$numoftrials[zfinal$subID==subs[j]] / t
}

ggplot(zfinal,aes(x=factor(subID),y=percent,color=factor(group),fill=factor(group)))+
  geom_bar(stat="identity")+
  labs(x = "Subject", y = "% of trials")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  guides(color=FALSE)+
  scale_fill_brewer(palette="Set3",name="Trial breakdown",breaks=c("1","2","3"),labels=c("no AEM", "incorrect AEMs","correct AEMs"))+
  scale_color_brewer(palette="Set3")+
  scale_y_continuous(label=percent,limits=c(0,1),breaks=seq(0,1,.2))+
  theme(legend.position = "bottom")
```

AEM breakdown by block and switch
```{r}
z1 <- ddply(orig.sample3,.(subID,block,switch),summarise,trials=length(unique(TRIAL_INDEX,na.rm = TRUE)))  
z2 <- ddply(z1,.(block,switch),summarise,trials=sum(trials,na.rm = TRUE))
z2$group <- 1
names(z2)[3] <- "trials"

#breaking it down for correct and incorrect
#type 1 = correct AEM to target, 2 = incorrect AEM to distractor, 3 = no AEM
z3 <- ddply(aembreakdown,.(subID,block,switch,type),summarise,numoftrials=length(unique(trialnum,na.rm = TRUE)))  
z3 <- subset(z3, type < 3) #only want correct and incorrect
z4 <- subset(z3, type==1)
z4$type <- NULL
z4$group <- 3

z5 <- subset(z3, type==2)
z5$type <- NULL
z5$group <- 2

z4 <- read.csv("/Volumes/emberson/ResearchProjects/Pupillometry/Pinwheels/Data/aem_group3_feb7.csv") 
z5 <- read.csv("/Volumes/emberson/ResearchProjects/Pupillometry/Pinwheels/Data/aem_group2_feb7.csv") 

z6 <- ddply(z4,.(block,switch),summarise,trials=sum(numoftrials,na.rm = TRUE)) #correct
z6$group <- 3
z7 <- ddply(z5,.(block,switch),summarise,trials=sum(numoftrials,na.rm = TRUE)) #incorrect
z7$group <- 2

#group 1 = all trials, group 2 = incorrect, group 3= correct
z2$trials <- z2$trials - z6$trials - z7$trials

zfinal <- rbind(z2,z6,z7)
split <- c(`1` = "block 1",`2` = "block 2",`3` = "block 3")

ggplot(zfinal,aes(x=factor(switch),y=trials,fill=factor(group),color=factor(group)))+
  geom_bar(stat="identity")+
  labs(y = "Number of trials")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20),axis.title.x=element_blank())+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  guides(color=FALSE)+facet_wrap(~block,labeller = as_labeller(split))+
  theme(strip.text = element_text(size=16))+
  scale_x_discrete(breaks=c("1","2"),labels=c("pre-switch", "post-switch"))+
  scale_y_continuous(limits=c(0,200),breaks=seq(0,200,25))+
  scale_fill_brewer(palette="Set3",name="Trial breakdown",breaks=c("1","2","3"),labels=c("no AEM", "incorrect AEMs","correct AEMs"))+
  scale_color_brewer(palette="Set3")+
  theme(legend.position = "bottom")

#just looking at AEM trials
zfinal2 <- subset(zfinal, group > 1)
split <- c(`1` = "block 1",`2` = "block 2",`3` = "block 3")

ggplot(zfinal2,aes(x=factor(switch),y=trials,fill=factor(group),color=factor(group)))+
  geom_bar(stat="identity")+
  labs(y = "Number of trials")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20),axis.title.x=element_blank())+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  guides(color=FALSE)+
  facet_wrap(~block,labeller = as_labeller(split))+
  theme(strip.text = element_text(size=16))+
  scale_x_discrete(breaks=c("1","2"),labels=c("pre-switch", "post-switch"))+
  scale_y_continuous(limits=c(0,40),breaks=seq(0,40,5))+
  scale_color_manual(values = c("#fffcb7", "#bebad9"))+
  scale_fill_manual(values = c("#fffcb7", "#bebad9"),name="Trial breakdown",breaks=c("2","3"),labels=c("incorrect AEMs","correct AEMs"))+
  theme(legend.position = "bottom")

#just looking at AEM trials version 2
zfinal2 <- subset(zfinal, group > 1)
split <- c(`1` = "block 1",`2` = "block 2",`3` = "block 3")
dodge <- position_dodge(width=0.9)

ggplot(zfinal2,aes(x=factor(switch),y=trials,fill=factor(group),color=factor(group)))+
  geom_bar(stat="identity",position=dodge)+
  labs(y = "Number of trials")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0))+
  theme(axis.title = element_text(face="bold", size=16),axis.title.x=element_blank())+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  guides(color=FALSE)+
  facet_wrap(~block,labeller = as_labeller(split))+
  theme(strip.text = element_text(size=16))+
  scale_x_discrete(breaks=c("1","2"),labels=c("pre-switch", "post-switch"))+
  scale_y_continuous(limits=c(0,25),breaks=seq(0,25,5))+
  scale_color_manual(values = c("#fffcb7", "#bebad9"))+
  scale_fill_manual(values = c("#fffcb7", "#bebad9"),name="Trial breakdown",breaks=c("2","3"),labels=c("incorrect AEMs","correct AEMs"))+
  theme(legend.position = "bottom")

```

for correct and incorrect AEM, count number of babies in each subblock
```{r}
#type 1 = correct AEM to target, 2 = incorrect AEM to distractor, 3 = no AEM
e1 <- subset(aembreakdown, type < 3)
e2 <- ddply(e1,.(subID,trialnum2,block,switch),summarise,type=mean(type))  
e3 <- ddply(e2,.(block,switch,type),summarise,numofbabies = length(unique(subID,na.rm = TRUE)))
e3$group <- 3
e3$group[e3$type==2] <- 2
dodge <- position_dodge(width=0.9)
split <- c(`1` = "block 1",`2` = "block 2",`3` = "block 3")

ggplot(e3,aes(x=factor(switch),y=numofbabies,fill=factor(group),color=factor(group)))+
  geom_bar(stat="identity")+
  labs(y = "Number of babies")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0))+
  theme(axis.title = element_text(face="bold", size=16),axis.title.x=element_blank())+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  scale_x_discrete(breaks=c("1","2"),labels=c("pre-switch", "post-switch"))+
  facet_wrap(~block,labeller = as_labeller(split))+
  theme(strip.text = element_text(size=16))+
  guides(color=FALSE)+
  scale_color_manual(values = c("#fffcb7", "#bebad9"))+
  scale_fill_manual(values = c("#fffcb7", "#bebad9"),name="Trial breakdown",breaks=c("2","3"),labels=c("incorrect AEMs","correct AEMs"))+
  scale_y_continuous(limits=c(0,25),breaks=seq(0,25,5))+
  theme(legend.position = "bottom")

#focusing on just correct AEM
e1 <- subset(aembreakdown, type ==1)
e2 <- ddply(e1,.(subID,block,trialnum,trialnum2,switch),summarise,type=mean(type))  
e3 <- ddply(e2,.(subID,block,switch),summarise,numofaem = length(unique(trialnum,na.rm = TRUE)))

split <- c(`1` = "block 1",`2` = "block 2",`3` = "block 3")

ggplot(e3,aes(x=factor(switch),y=numofaem,fill=factor(subID),color=factor(subID)))+
  geom_bar(stat="identity")+
  labs(y = "Number of correct AEMs")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0))+
  theme(axis.title = element_text(face="bold", size=16),axis.title.x=element_blank())+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  scale_x_discrete(breaks=c("1","2"),labels=c("pre-switch", "post-switch"))+
  facet_wrap(~block,labeller = as_labeller(split))+
  theme(strip.text = element_text(size=16))+
  guides(color=FALSE)+
  scale_y_continuous(limits=c(0,25),breaks=seq(0,25,5))+
  theme(legend.position = "none")

#focusing on just incorrect AEM
e1 <- subset(aembreakdown, type ==2)
e2 <- ddply(e1,.(subID,block,trialnum,trialnum2,switch),summarise,type=mean(type))  
e3 <- ddply(e2,.(subID,block,switch),summarise,numofaem = length(unique(trialnum,na.rm = TRUE)))

split <- c(`1` = "block 1",`2` = "block 2",`3` = "block 3")

ggplot(e3,aes(x=factor(switch),y=numofaem,fill=factor(subID),color=factor(subID)))+
  geom_bar(stat="identity")+
  labs(y = "Number of incorrect AEMs")+
  theme(plot.title = element_text(face="bold", size=16, hjust=0))+
  theme(axis.title = element_text(face="bold", size=16),axis.title.x=element_blank())+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  scale_x_discrete(breaks=c("1","2"),labels=c("pre-switch", "post-switch"))+
  facet_wrap(~block,labeller = as_labeller(split))+
  theme(strip.text = element_text(size=16))+
  guides(color=FALSE)+
  theme(legend.position = "none")+
  scale_y_continuous(limits=c(0,25),breaks=seq(0,25,5))
```

count number of aems (correct and incorrect) for each subject, separate it for each subblock
```{r}
#type 1 = correct AEM to target, 2 = incorrect AEM to distractor, 3 = no AEM
#correct
e1 <- subset(aembreakdown, type ==1)
e2 <- ddply(e1,.(subID,block,trialnum,trialnum2,switch),summarise,type=mean(type))  
e3 <- ddply(e2,.(subID,block,switch),summarise,numofaem = length(unique(trialnum,na.rm = TRUE)))
e3$sublock[e3$block==1 & e3$switch==1] <- 1
e3$sublock[e3$block==1 & e3$switch==2] <- 2
e3$sublock[e3$block==2 & e3$switch==1] <- 3
e3$sublock[e3$block==2 & e3$switch==2] <- 4
e3$sublock[e3$block==3 & e3$switch==1] <- 5
e3$sublock[e3$block==3 & e3$switch==2] <- 6

ggplot(e3,aes(x=factor(subID),y=numofaem,fill=factor(sublock),color=factor(sublock)))+
  geom_bar(stat="identity")+
  ggtitle("Correct AEMs")+
  labs(x = "Subject", y = "Number of trials")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  scale_fill_brewer(palette="YlGn",name="Subblock")+
  scale_color_brewer(palette="YlGn")+
  scale_y_continuous(limits=c(0,14),breaks=seq(0,14,1))+
  guides(color=FALSE)+
  theme(legend.position = "bottom")

#incorrect
e1 <- subset(aembreakdown, type ==2)
e2 <- ddply(e1,.(subID,block,trialnum,trialnum2,switch),summarise,type=mean(type))  
e3 <- ddply(e2,.(subID,block,switch),summarise,numofaem = length(unique(trialnum,na.rm = TRUE)))
e3$sublock[e3$block==1 & e3$switch==1] <- 1
e3$sublock[e3$block==1 & e3$switch==2] <- 2
e3$sublock[e3$block==2 & e3$switch==1] <- 3
e3$sublock[e3$block==2 & e3$switch==2] <- 4
e3$sublock[e3$block==3 & e3$switch==1] <- 5
e3$sublock[e3$block==3 & e3$switch==2] <- 6

ggplot(e3,aes(x=factor(subID),y=numofaem,fill=factor(sublock),color=factor(sublock)))+
  geom_bar(stat="identity")+
  ggtitle("Incorrect AEMs")+
  labs(x = "Subject", y = "Number of trials")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  scale_fill_brewer(palette="YlOrBr",name="Subblock")+
  scale_color_brewer(palette="YlOrBr")+
  scale_y_continuous(limits=c(0,14),breaks=seq(0,14,1))+
  guides(color=FALSE)+
  theme(legend.position = "bottom")
```

CONCLUSION: We will include block 3

play around with exclusion criteria, see how many babies we would exclude
1. each subject has to contribute at least one trial for preswitch and postswitch
2. each subject has to contribute at least one trial for preswitch and postswitch, for every block
3. each subject has to contribute at least one trial for preswitch and postswitch, for 2/3 blocks

```{r}
#criteria 1. each subject has to contribute at least one trial for preswitch and postswitch
#criteria 2. each subject has to contribute at least one trial for preswitch and postswitch, for every block
#criteria 3. each subject has to contribute at least one trial for preswitch and postswitch, for 2/3 blocks

#counting number of babies for criteria 1
cr1 <- ddply(orig.sample3,.(subID,switch),summarise,trials=length(unique(TRIAL_INDEX)))
#fail: 22 (1 sub exclude)

#counting number of babies for criteria 2
cr2 <- ddply(orig.sample3,.(subID,switch,block),summarise,trials=length(unique(TRIAL_INDEX)))
#fail: 3, 4, 6, 15, 16, 17, 19, 22, 26, 27, 29, 30 (12 subs excluded)

#counting number of babies for criteria 3
cr3 <- ddply(orig.sample3,.(subID,switch,block),summarise,trials=length(unique(TRIAL_INDEX)))
#fail: 3, 4, 16, 19, 22, 27, 29, 30 (8 subs excluded)

cr4 <- data.frame(critera = numeric(6),includeexclude = numeric(6), numbabies = numeric(6))
cr4$critera <- rep(1:3, each=2)
cr4$critera2[cr4$critera==1] <- "contribute at least one trial for 2/6 subblock (1 for preswitch and 1 for postswitch)"
cr4$critera2[cr4$critera==2] <- "contribute at least one trial for 6/6 subblock"
cr4$critera2[cr4$critera==3] <- "contribute at least one trial for 4/6 subblock (2 for preswitch and 2 for postswitch)"
cr4$includeexclude <- rep(1:2) #1=include, 2=exclude
cr4$numbabies[1] <- 33
cr4$numbabies[2] <- 1
cr4$numbabies[3] <- 22
cr4$numbabies[4] <- 12
cr4$numbabies[5] <- 26
cr4$numbabies[6] <- 8

ggplot(cr4,aes(x=factor(critera2),y=numbabies,fill=factor(includeexclude),color=factor(includeexclude)))+
  geom_bar(stat="identity")+
  ggtitle("Exclusion criteria")+
  labs(x = "Criteria", y = "Number of babies")+
  theme(plot.title = element_text(face="bold", size=14, hjust=0))+
  theme(axis.title = element_text(face="bold", size=16))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  scale_fill_brewer(palette="PuRd",name="Type",breaks=c("1","2"),labels=c("include", "exclude"))+
  scale_color_brewer(palette="PuRd")+
  scale_y_continuous(limits=c(0,34),breaks=seq(0,34,2))+
  guides(color=FALSE)+
  scale_x_discrete(labels = wrap_format(40))+
  theme(legend.position = "bottom")
```

Number of babies / percent of babies that make AEM for each trial graph
facet _wrap by switch, x = trial number, color = incorrect vs correct
#type 1 = correct AEM to target, 2 = incorrect AEM to distractor, 3 = no AEM
```{r}
#number of babies
b1 <- ddply(aembreakdown,.(block,switch,trialnum2,type),summarise,numbabies=length(unique(subID)))
b1 <- subset(b1, type <3)

b2 <- ddply(b1,.(trialnum2,switch,type),summarise,meannum=mean(numbabies),
            sdnum = sd(numbabies, na.rm = TRUE)/sqrt(length(numbabies)))
b2$group[b2$type==2] <- 2
b2$group[b2$type==1] <- 3

dodge <- position_dodge(width=0.9)
limits <- aes(ymax = meannum + sdnum, ymin=meannum - sdnum)
split <- c(`1` = "Preswitch",`2` = "Postswitch")

ggplot(b2,aes(x=factor(trialnum2),y=meannum,fill=factor(group),color=factor(group)))+
  geom_bar(stat="identity",position=dodge)+
  labs(x = "Trial number", y = "Number of babies")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  guides(color=FALSE)+
  geom_errorbar(limits, width=0.25,position = position_dodge(0.9),color="black")+
  facet_wrap(~switch,labeller = as_labeller(split),dir="v")+
  scale_color_manual(values = c("#fffcb7", "#bebad9"))+
  scale_fill_manual(values = c("#fffcb7", "#bebad9"),name="AEM Type",breaks=c("2","3"),labels=c("incorrect AEMs","correct AEMs"))+
  theme(strip.text = element_text(size=16))+
  scale_y_continuous(limits=c(0,7),breaks=seq(0,7,1))

#percent of babies

```
