---
title: "Jan 4 2018 pupil"
author: "Felicia Zhang"
date: '2018-01-06'
output: html_document
---

Timecourse graph: Around 1000-2700ms is where we see this difference in pupil size, 
According to Jan10Analysis, we see that there isn’t really a difference in x coordinates during that time, which is good. It means the difference in pupil size is not related to looking differences.
but just to double check we should look at eccentricity (or absolute from center for x-coordinate)
if the differences collapses then we're good

look at eccentricity
1. graphs (60-63): 
a. calculate absolute from center for x-coordinate  
b. slide 62,63 groups should be divided by preswitch aem groups

do percentage of trials for AEM bc there are differences in num of trials/baby

if baseline is good, then think about how we want to measure stat difference

```{r setup, include=FALSE}
library(ggplot2) 
library(zoo)
library(reshape)
library(plyr)
library(scales) 
library(data.table)
library(signal)
library(matrixStats)
library(lme4)
library(arm)
library(RColorBrewer)
library(lmerTest)
library(boot)

#load preprocessed data
#Oct21 has PUPIL_CORRECTED_2 calculated using 0-1500ms
orig.sample <- read.csv("/Volumes/emberson/ResearchProjects/Pupillometry/Pinwheels/Data/Pinwheel_Infant_Preprocessed_AllSamples_Nov28.csv") #Nov28 has trackloss % for all trials
orig.sample2 <- read.csv("/Volumes/emberson/ResearchProjects/Pupillometry/Pinwheels/Data/Pinwheel_Infant_Preprocessed_RemovedOutliers_Nov28.csv")  #Nov28 has bad trials removed
orig.sample$X <- NULL
orig.sample2$X <- NULL
orig.sample$X.1 <- NULL
orig.sample2$X.1 <- NULL

#REMOVE TRIALS 5-8 FOR EACH SUBBLOCK
orig.sample$trialnum <- 0
orig.sample$trialnum[orig.sample$TRIAL_INDEX == 1 | orig.sample$TRIAL_INDEX == 9 | orig.sample$TRIAL_INDEX == 17 | orig.sample$TRIAL_INDEX == 25 | orig.sample$TRIAL_INDEX == 33 | orig.sample$TRIAL_INDEX == 41] <- 1
orig.sample$trialnum[orig.sample$TRIAL_INDEX == 2 | orig.sample$TRIAL_INDEX == 10 | orig.sample$TRIAL_INDEX == 18 | orig.sample$TRIAL_INDEX == 26 | orig.sample$TRIAL_INDEX == 34 | orig.sample$TRIAL_INDEX == 42] <- 2
orig.sample$trialnum[orig.sample$TRIAL_INDEX == 3 | orig.sample$TRIAL_INDEX == 11 | orig.sample$TRIAL_INDEX == 19 | orig.sample$TRIAL_INDEX == 27 | orig.sample$TRIAL_INDEX == 35 | orig.sample$TRIAL_INDEX == 43] <- 3
orig.sample$trialnum[orig.sample$TRIAL_INDEX == 4 | orig.sample$TRIAL_INDEX == 12 | orig.sample$TRIAL_INDEX == 20 | orig.sample$TRIAL_INDEX == 28 | orig.sample$TRIAL_INDEX == 36 | orig.sample$TRIAL_INDEX == 44] <- 4
orig.sample$trialnum[orig.sample$TRIAL_INDEX == 5 | orig.sample$TRIAL_INDEX == 13 | orig.sample$TRIAL_INDEX == 21 | orig.sample$TRIAL_INDEX == 29 | orig.sample$TRIAL_INDEX == 37 | orig.sample$TRIAL_INDEX == 45] <- 5
orig.sample$trialnum[orig.sample$TRIAL_INDEX == 6 | orig.sample$TRIAL_INDEX == 14 | orig.sample$TRIAL_INDEX == 22 | orig.sample$TRIAL_INDEX == 30 | orig.sample$TRIAL_INDEX == 38 | orig.sample$TRIAL_INDEX == 46] <- 6
orig.sample$trialnum[orig.sample$TRIAL_INDEX == 7 | orig.sample$TRIAL_INDEX == 15 | orig.sample$TRIAL_INDEX == 23 | orig.sample$TRIAL_INDEX == 31 | orig.sample$TRIAL_INDEX == 39 | orig.sample$TRIAL_INDEX == 47] <- 7
orig.sample$trialnum[orig.sample$TRIAL_INDEX == 8 | orig.sample$TRIAL_INDEX == 16 | orig.sample$TRIAL_INDEX == 24 | orig.sample$TRIAL_INDEX == 32 | orig.sample$TRIAL_INDEX == 40 | orig.sample$TRIAL_INDEX == 48] <- 8

orig.sample2$trialnum <- 0
orig.sample2$trialnum[orig.sample2$TRIAL_INDEX == 1 | orig.sample2$TRIAL_INDEX == 9 | orig.sample2$TRIAL_INDEX == 17 | orig.sample2$TRIAL_INDEX == 25 | orig.sample2$TRIAL_INDEX == 33 | orig.sample2$TRIAL_INDEX == 41] <- 1
orig.sample2$trialnum[orig.sample2$TRIAL_INDEX == 2 | orig.sample2$TRIAL_INDEX == 10 | orig.sample2$TRIAL_INDEX == 18 | orig.sample2$TRIAL_INDEX == 26 | orig.sample2$TRIAL_INDEX == 34 | orig.sample2$TRIAL_INDEX == 42] <- 2
orig.sample2$trialnum[orig.sample2$TRIAL_INDEX == 3 | orig.sample2$TRIAL_INDEX == 11 | orig.sample2$TRIAL_INDEX == 19 | orig.sample2$TRIAL_INDEX == 27 | orig.sample2$TRIAL_INDEX == 35 | orig.sample2$TRIAL_INDEX == 43] <- 3
orig.sample2$trialnum[orig.sample2$TRIAL_INDEX == 4 | orig.sample2$TRIAL_INDEX == 12 | orig.sample2$TRIAL_INDEX == 20 | orig.sample2$TRIAL_INDEX == 28 | orig.sample2$TRIAL_INDEX == 36 | orig.sample2$TRIAL_INDEX == 44] <- 4
orig.sample2$trialnum[orig.sample2$TRIAL_INDEX == 5 | orig.sample2$TRIAL_INDEX == 13 | orig.sample2$TRIAL_INDEX == 21 | orig.sample2$TRIAL_INDEX == 29 | orig.sample2$TRIAL_INDEX == 37 | orig.sample2$TRIAL_INDEX == 45] <- 5
orig.sample2$trialnum[orig.sample2$TRIAL_INDEX == 6 | orig.sample2$TRIAL_INDEX == 14 | orig.sample2$TRIAL_INDEX == 22 | orig.sample2$TRIAL_INDEX == 30 | orig.sample2$TRIAL_INDEX == 38 | orig.sample2$TRIAL_INDEX == 46] <- 6
orig.sample2$trialnum[orig.sample2$TRIAL_INDEX == 7 | orig.sample2$TRIAL_INDEX == 15 | orig.sample2$TRIAL_INDEX == 23 | orig.sample2$TRIAL_INDEX == 31 | orig.sample2$TRIAL_INDEX == 39 | orig.sample2$TRIAL_INDEX == 47] <- 7
orig.sample2$trialnum[orig.sample2$TRIAL_INDEX == 8 | orig.sample2$TRIAL_INDEX == 16 | orig.sample2$TRIAL_INDEX == 24 | orig.sample2$TRIAL_INDEX == 32 | orig.sample2$TRIAL_INDEX == 40 | orig.sample2$TRIAL_INDEX == 48] <- 8

orig.sample3 <- subset(orig.sample, trialnum < 5)
orig.sample4 <- subset(orig.sample2, trialnum < 5)

#orig.sample = all trials
#orig.sample2 = trials with more than 50% looking
#orig.sample3 = orig.sample but only trials 1-4 of each subblock
#orig.sample4 = orig.sample2 but only trials 1-4 of each subblock
#orig.sample5 = orig.sample3 but without block 3
#orig.sample6 = orig.sample4 but without block 3
#orig.sample7 = orig.sample5 but without trial 1 of each sublock
#orig.sample8 = orig.sample6 but without trial 1 of each sublock

#also remove block 3
orig.sample5 <- subset(orig.sample3, block < 3)
orig.sample6 <- subset(orig.sample4, block < 3)
#also remove trial 1 of every sublock
orig.sample7 <- subset(orig.sample5, trialnum > 1)
orig.sample8 <- subset(orig.sample6, trialnum > 1)
```

main timecourse plot
```{r}
# screen res is 1024 x 1280 (Y X)
#a. Y coordinate timecourse, pre and post
#line graph
boo1 <- ddply(orig.sample8,.(subID,switch,TIMECODE),summarise,pupil=mean(PUPIL_CORRECTED,na.rm = TRUE)) #collapse across trials
boo2 <- ddply(boo1,.(switch,TIMECODE),summarise,pupilavg=mean(pupil,na.rm = TRUE),sepupil=sd(pupil, na.rm = TRUE)/sqrt(length(pupil))) #collapse across subs
vlines <- c(250,1750,2550)

ggplot(boo2,aes(x=TIMECODE,y=pupilavg,color=factor(switch),fill=factor(switch)))+
  geom_line()+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("Timecourse: Pupil Change")+
  labs(x = "Time", y = "Pupil change from baseline (%)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  geom_ribbon(aes(ymin=pupilavg-sepupil,ymax=pupilavg+sepupil),alpha=0.4)+
  geom_vline(xintercept = vlines)+
  scale_x_continuous(limits=c(0,4000),breaks=seq(0,4000,500), expand = c(0, 0))+
  scale_fill_discrete(name="Switch",breaks=c("1", "2"),labels=c("Pre-Switch", "Post-Switch"))+guides(color=FALSE)+
  scale_y_continuous(labels=percent,limits=c(-0.1,.1),breaks=seq(-0.1,.1,.02), expand = c(0, 0))

#facet_Wrap by block
#line graph
boo1 <- ddply(orig.sample8,.(subID,block,switch,TIMECODE),summarise,pupil=mean(PUPIL_CORRECTED,na.rm = TRUE)) #collapse across trials
boo2 <- ddply(boo1,.(block,switch,TIMECODE),summarise,pupilavg=mean(pupil,na.rm = TRUE),sepupil=sd(pupil, na.rm = TRUE)/sqrt(length(pupil))) #collapse across subs
vlines <- c(250,1750,2550)

ggplot(boo2,aes(x=TIMECODE,y=pupilavg,color=factor(switch),fill=factor(switch)))+
  geom_line()+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("Timecourse: Pupil Change")+
  labs(x = "Time", y = "Pupil change from baseline (%)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  geom_ribbon(aes(ymin=pupilavg-sepupil,ymax=pupilavg+sepupil),alpha=0.4)+
  geom_vline(xintercept = vlines)+
  scale_x_continuous(limits=c(0,4000),breaks=seq(0,4000,500), expand = c(0, 0))+
  scale_fill_discrete(name="Switch",breaks=c("1", "2"),labels=c("Pre-Switch", "Post-Switch"))+guides(color=FALSE)+
  facet_wrap(~block,dir="v")+
  scale_y_continuous(labels=percent,limits=c(-0.2,.2),breaks=seq(-0.2,.2,.05), expand = c(0, 0))

```

how many trials included per baby
```{r}
d1 <- ddply(orig.sample8,.(subID,switch,block,TRIAL_INDEX,trialnum),summarise,rawpupil=mean(RIGHT_PUPIL_SIZE,na.rm = TRUE)) #collapse across trials
d2 <- ddply(d1,.(subID,switch),summarise,numtrials=length(unique(TRIAL_INDEX)))

ggplot(d2,aes(x=factor(subID),y=numtrials,color=factor(switch),fill=factor(switch)))+
  geom_bar(stat="identity")+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("How many trials included per baby")+
  labs(x = "Subject", y = "Number of trials")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  scale_y_continuous(limits=c(0,12),breaks=seq(0,12,2))+
  guides(color=FALSE)+
  scale_fill_discrete(name="Switch",breaks=c("1","2"),labels=c("Pre-Switch", "Post-Switch"))

d3 <- ddply(d1,.(subID,switch,block),summarise,numtrials=length(unique(TRIAL_INDEX)))

ggplot(d3,aes(x=factor(subID),y=numtrials,color=factor(switch),fill=factor(switch)))+
  geom_bar(stat="identity")+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("How many trials included per baby")+
  labs(x = "Subject", y = "Number of trials")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  scale_y_continuous(limits=c(0,6),breaks=seq(0,6,1))+
  guides(color=FALSE)+
  scale_fill_discrete(name="Switch",breaks=c("1","2"),labels=c("Pre-Switch", "Post-Switch"))+
  facet_wrap(~block,dir="v")

```

check counterbalancing order
```{r}
#1 = left, 2 = right
hoo <- ddply(orig.sample8,.(subID,block,switch),summarise,targetside=mean(leftright,na.rm = TRUE)) #collapse across trials
newData1 <- data.frame(subID = "3", block = "1", switch = "1", targetside = "0")
newData2 <- data.frame(subID = "3", block = "2", switch = "2", targetside = "0")
newData3 <- data.frame(subID = "4", block = "1", switch = "2", targetside = "0")
newData4 <- data.frame(subID = "6", block = "2", switch = "2", targetside = "0")
newData5 <- data.frame(subID = "7", block = "1", switch = "1", targetside = "0")
newData6 <- data.frame(subID = "7", block = "2", switch = "1", targetside = "0")
newData7 <- data.frame(subID = "11", block = "2", switch = "1", targetside = "0")
newData8 <- data.frame(subID = "13", block = "2", switch = "1", targetside = "0")
newData9 <- data.frame(subID = "16", block = "1", switch = "1", targetside = "0")
newData10 <- data.frame(subID = "16", block = "2", switch = "2", targetside = "0")
newData11 <- data.frame(subID = "19", block = "2", switch = "2", targetside = "0")
newData12 <- data.frame(subID = "21", block = "2", switch = "2", targetside = "0")
newData13 <- data.frame(subID = "22", block = "1", switch = "2", targetside = "0")
newData14 <- data.frame(subID = "22", block = "2", switch = "1", targetside = "0")
newData15 <- data.frame(subID = "22", block = "2", switch = "2", targetside = "0")
newData16 <- data.frame(subID = "24", block = "1", switch = "1", targetside = "0")
newData17 <- data.frame(subID = "25", block = "2", switch = "2", targetside = "0")
newData18 <- data.frame(subID = "27", block = "1", switch = "1", targetside = "0")
newData19 <- data.frame(subID = "27", block = "2", switch = "1", targetside = "0")
newData20 <- data.frame(subID = "27", block = "2", switch = "2", targetside = "0")
newData21 <- data.frame(subID = "29", block = "1", switch = "2", targetside = "0")
newData22 <- data.frame(subID = "29", block = "2", switch = "1", targetside = "0")
newData23 <- data.frame(subID = "29", block = "2", switch = "2", targetside = "0")
newData24 <- data.frame(subID = "30", block = "1", switch = "1", targetside = "0")
newData25 <- data.frame(subID = "30", block = "1", switch = "2", targetside = "0")
newData26 <- data.frame(subID = "30", block = "2", switch = "2", targetside = "0")
newData27 <- data.frame(subID = "31", block = "1", switch = "1", targetside = "0")
newData28 <- data.frame(subID = "33", block = "2", switch = "2", targetside = "0")

hoo <- rbind( hoo[1:8,], newData1, hoo[9:108,] )
hoo <- rbind( hoo[1:11,], newData2, hoo[12:109,] )
hoo <- rbind( hoo[1:13,], newData3, hoo[14:110,] )
hoo <- rbind( hoo[1:23,], newData4, hoo[24:111,] )
hoo <- rbind( hoo[1:24,], newData5, hoo[25:112,] )
hoo <- rbind( hoo[1:26,], newData6, hoo[27:113,] )
hoo <- rbind( hoo[1:42,], newData7, hoo[43:114,] )
hoo <- rbind( hoo[1:50,], newData8, hoo[51:115,] )
hoo <- rbind( hoo[1:60,], newData9, hoo[61:116,] )
hoo <- rbind( hoo[1:63,], newData10, hoo[64:117,] )
hoo <- rbind( hoo[1:75,], newData11, hoo[76:118,] )
hoo <- rbind( hoo[1:83,], newData12, hoo[84:119,] )
hoo <- rbind( hoo[1:85,], newData13, hoo[86:120,] )
hoo <- rbind( hoo[1:86,], newData14, hoo[87:121,] )
hoo <- rbind( hoo[1:87,], newData15, hoo[88:122,] )

hoo <- rbind( hoo[1:92,], newData16, hoo[93:123,] )
hoo <- rbind( hoo[1:99,], newData17, hoo[100:124,] )
hoo <- rbind( hoo[1:104,], newData18, hoo[105:125,] )
hoo <- rbind( hoo[1:106,], newData19, hoo[107:126,] )
hoo <- rbind( hoo[1:107,], newData20, hoo[108:127,] )
hoo <- rbind( hoo[1:113,], newData21, hoo[114:128,] )
hoo <- rbind( hoo[1:114,], newData22, hoo[115:129,] )
hoo <- rbind( hoo[1:115,], newData23, hoo[116:130,] )
hoo <- rbind( hoo[1:116,], newData24, hoo[117:131,] )
hoo <- rbind( hoo[1:117,], newData25, hoo[118:132,] )
hoo <- rbind( hoo[1:119,], newData26, hoo[120:133,] )
hoo <- rbind( hoo[1:120,], newData27, hoo[121:134,] )
hoo <- rbind( hoo[1:131,], newData28, hoo[132:135,] )

hoo$value <- rep(1:4)
#CREATED GRAPH IN EXCEL

```

raw pupil size for preswitch and post switch
```{r}
# screen res is 1024 x 1280 (Y X)
#a. Y coordinate timecourse, pre and post
#line graph
boo1 <- ddply(orig.sample8,.(subID,switch,TIMECODE),summarise,rawpupil=mean(RIGHT_PUPIL_SIZE,na.rm = TRUE)) #collapse across trials
boo2 <- ddply(boo1,.(switch,TIMECODE),summarise,rawpupilavg=mean(rawpupil,na.rm = TRUE),serawpupil=sd(rawpupil, na.rm = TRUE)/sqrt(length(rawpupil))) #collapse across subs
vlines <- c(250,1750,2550)

ggplot(boo2,aes(x=TIMECODE,y=rawpupilavg,color=factor(switch),fill=factor(switch)))+
  geom_line()+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("Timecourse of raw pupil size")+
  labs(x = "Time", y = "Raw pupil size")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  geom_ribbon(aes(ymin=rawpupilavg-serawpupil,ymax=rawpupilavg+serawpupil),alpha=0.4)+
  geom_vline(xintercept = vlines)+
  scale_x_continuous(limits=c(0,4000),breaks=seq(0,4000,500), expand = c(0, 0))+
  scale_fill_discrete(name="Switch",breaks=c("1", "2"),labels=c("Pre-Switch", "Post-Switch"))+guides(color=FALSE)+
  scale_y_continuous(limits=c(2000,4000),breaks=seq(2000,4000,200), expand = c(0, 0))

#facet_Wrap by block
#line graph
boo1 <- ddply(orig.sample8,.(subID,block,switch,TIMECODE),summarise,rawpupil=mean(RIGHT_PUPIL_SIZE,na.rm = TRUE)) #collapse across trials
boo2 <- ddply(boo1,.(block,switch,TIMECODE),summarise,rawpupilavg=mean(rawpupil,na.rm = TRUE),serawpupil=sd(rawpupil, na.rm = TRUE)/sqrt(length(rawpupil))) #collapse across subs
vlines <- c(250,1750,2550)

ggplot(boo2,aes(x=TIMECODE,y=rawpupilavg,color=factor(switch),fill=factor(switch)))+
  geom_line()+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("Timecourse of raw pupil size")+
  labs(x = "Time", y = "Raw pupil size")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  geom_ribbon(aes(ymin=rawpupilavg-serawpupil,ymax=rawpupilavg+serawpupil),alpha=0.4)+
  geom_vline(xintercept = vlines)+
  scale_x_continuous(limits=c(0,4000),breaks=seq(0,4000,500), expand = c(0, 0))+
  scale_fill_discrete(name="Switch",breaks=c("1", "2"),labels=c("Pre-Switch", "Post-Switch"))+guides(color=FALSE)+
  facet_wrap(~block, dir="v")+
  scale_y_continuous(limits=c(2000,4200),breaks=seq(2000,4200,200), expand = c(0, 0))

```

look at eccentricity: calculate absolute from center for x-coordinate for graphs (51,52)
screen res is 1024 x 1280 (Y X)
middle is 640
```{r}
#calculate absolute x coordinate from center
coo <- orig.sample8
coo$RIGHT_GAZE_X2 <- abs(coo$RIGHT_GAZE_X-640)

boo1 <- ddply(coo,.(subID,switch,TIMECODE),summarise,absX=mean(RIGHT_GAZE_X2,na.rm = TRUE)) #collapse across trials
boo2 <- ddply(boo1,.(switch,TIMECODE),summarise,absXavg=mean(absX,na.rm = TRUE),seabsX=sd(absX, na.rm = TRUE)/sqrt(length(absX))) #collapse across subs
vlines <- c(250,1750,2550)

ggplot(boo2,aes(x=TIMECODE,y=absXavg,color=factor(switch),fill=factor(switch)))+
  geom_line()+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("Timecourse of X coordinate")+
  labs(x = "Time", y = "Absolute distance from center")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  geom_ribbon(aes(ymin=absXavg-seabsX,ymax=absXavg+seabsX),alpha=0.4)+
  geom_vline(xintercept = vlines)+
  scale_x_continuous(limits=c(0,4000),breaks=seq(0,4000,500), expand = c(0, 0))+
  scale_fill_discrete(name="Switch",breaks=c("1", "2"),labels=c("Pre-Switch", "Post-Switch"))+guides(color=FALSE)+
  scale_y_continuous(limits=c(0,400),breaks=seq(0,400,50), expand = c(0, 0))

boo1 <- ddply(coo,.(subID,switch,TIMECODE,block),summarise,xcoordinate=mean(RIGHT_GAZE_X2,na.rm = TRUE)) #collapse across trials
boo2 <- ddply(boo1,.(switch,TIMECODE,block),summarise,Xavg=mean(xcoordinate,na.rm = TRUE),seX=sd(xcoordinate, na.rm = TRUE)/sqrt(length(xcoordinate))) #collapse across subs
vlines <- c(250,1750,2550)

ggplot(boo2,aes(x=TIMECODE,y=Xavg,color=factor(switch),fill=factor(switch)))+
  geom_line()+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("Timecourse of X coordinate")+
  labs(x = "Time", y = "Absolute distance from center")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  geom_ribbon(aes(ymin=Xavg-seX,ymax=Xavg+seX),alpha=0.4)+
  geom_vline(xintercept = vlines)+
  scale_x_continuous(limits=c(0,4000),breaks=seq(0,4000,1000), expand = c(0, 0))+
  scale_y_continuous(limits=c(0,400),breaks=seq(0,400,50), expand = c(0, 0))+
  scale_fill_discrete(name="Switch",breaks=c("1", "2"),labels=c("Pre-Switch", "Post-Switch"))+guides(color=FALSE)+
  facet_wrap(~block)
```

graphs (72-75)
1. do percentage of trials for AEM bc there are differences in num of trials completed/baby
```{r}
#preparing dataframe
aembreakdown <- read.csv("/Volumes/emberson/ResearchProjects/Pupillometry/Pinwheels/Data/aembreakdown.csv") 

z1 <- subset(aembreakdown, lookattarget==1)
z1$numAEMfinal <- z1$numAEM
z0 <- subset(aembreakdown, lookattarget==0)
z0$numAEMfinal <- 3- z1$numAEM

for (i in 1:length(z0$subID)) {
  if (z0$numAEMfinal[i] > z0$numAEM[i]) {
    z0$numAEMfinal[i] <- 0
  }
}

z0$totalAEM <-z1$numAEMfinal+z0$numAEMfinal
z1$totalAEM <-z1$numAEMfinal+z0$numAEMfinal
z0$percentAEM <-z0$numAEMfinal/z0$totalAEM
z1$percentAEM <-z1$numAEMfinal/z1$totalAEM

zfinal <- rbind(z1,z0)
dodge <- position_dodge(width=0.9)

##preswitch vs post switch
v1 <- subset(zfinal, switch==1)
v2 <- subset(zfinal, switch==2)

v11 <- ddply(v1,.(subID,lookattarget,switch),summarise,num=sum(numAEMfinal,na.rm = TRUE),total=sum(totalAEM,na.rm = TRUE))
v21 <- ddply(v2,.(subID,lookattarget,switch),summarise,num=sum(numAEMfinal,na.rm = TRUE),total=sum(totalAEM,na.rm = TRUE))
vfinal <- rbind(v11,v21)
vfinal$percent <- vfinal$num/vfinal$total
split <- c(`1` = "PreSwitch",`2` = "PostSwitch")

#grouped together
hoo2 <- ddply(vfinal,.(switch,lookattarget),summarise,avgAEM=mean(percent,na.rm = TRUE),seAEM=sd(percent, na.rm = TRUE)/sqrt(length(percent)))
limits <- aes(ymax = avgAEM + seAEM, ymin=avgAEM - seAEM)

ggplot(hoo2,aes(x=factor(switch),y=avgAEM,fill=factor(lookattarget)))+
  geom_bar(stat="identity")+
  labs(y = "Percent of AEMs")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20),axis.title.x=element_blank())+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,0.2))+
  scale_x_discrete(breaks=c("1","2"),labels=c("pre-switch", "post-switch"))+
  scale_fill_discrete(name="AEM type",breaks=c("0","1"),labels=c("Distractor", "Target"))

#by subject
ggplot(vfinal,aes(x=factor(subID),y=percent,color=factor(lookattarget),fill=factor(lookattarget)))+geom_bar(stat="identity")+
  labs(x = "Subject", y = "Percent of AEMs")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,0.2))+
  guides(color=FALSE)+facet_wrap(~switch,dir="v",labeller = as_labeller(split))+
  theme(strip.text = element_text(size=16))+
  scale_fill_discrete(name="AEM type",breaks=c("0","1"),labels=c("Distractor", "Target"))
  
##block 1 vs block 2
v1 <- subset(zfinal, block==1)
v2 <- subset(zfinal, block==2)

v11 <- ddply(v1,.(subID,lookattarget,block),summarise,num=sum(numAEMfinal,na.rm = TRUE),total=sum(totalAEM,na.rm = TRUE))
v21 <- ddply(v2,.(subID,lookattarget,block),summarise,num=sum(numAEMfinal,na.rm = TRUE),total=sum(totalAEM,na.rm = TRUE))
vfinal <- rbind(v11,v21)
vfinal$percent <- vfinal$num/vfinal$total
split <- c(`1` = "Block 1",`2` = "Block 2")

#grouped together
hoo2 <- ddply(vfinal,.(block,lookattarget),summarise,avgAEM=mean(percent,na.rm = TRUE),seAEM=sd(percent, na.rm = TRUE)/sqrt(length(percent)))
limits <- aes(ymax = avgAEM + seAEM, ymin=avgAEM - seAEM)

ggplot(hoo2,aes(x=factor(block),y=avgAEM,fill=factor(lookattarget)))+
  geom_bar(stat="identity")+
  labs(y = "Percent of AEMs")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20),axis.title.x=element_blank())+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,0.2))+
  scale_x_discrete(breaks=c("1","2"),labels=c("Block 1", "Block 2"))+
  scale_fill_discrete(name="AEM type",breaks=c("0","1"),labels=c("Distractor", "Target"))

#by subject
ggplot(vfinal,aes(x=factor(subID),y=percent,color=factor(lookattarget),fill=factor(lookattarget)))+geom_bar(stat="identity")+
  labs(x = "Subject", y = "Percent of AEMs")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,0.2))+
  guides(color=FALSE)+facet_wrap(~block,dir="v",labeller = as_labeller(split))+
  theme(strip.text = element_text(size=16))+
  scale_fill_discrete(name="AEM type",breaks=c("0","1"),labels=c("Distractor", "Target"))
  
##look at interaction
#grouped together
hoo2 <- ddply(zfinal,.(block,switch,lookattarget),summarise,avgAEM=mean(percentAEM,na.rm = TRUE),seAEM=sd(percentAEM, na.rm = TRUE)/sqrt(length(percentAEM)))
split <- c(`1` = "Block 1",`2` = "Block 2")

ggplot(hoo2,aes(x=factor(switch),y=avgAEM,fill=factor(lookattarget)))+
  geom_bar(stat="identity")+
  labs(y = "Percent of AEMs")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20),axis.title.x=element_blank())+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  scale_y_continuous(labels=percent,limits=c(0,1),breaks=seq(0,1,0.2))+
  scale_x_discrete(breaks=c("1","2"),labels=c("pre-switch", "post-switch"))+
  scale_fill_discrete(name="AEM type",breaks=c("0","1"),labels=c("Distractor", "Target"))+
  facet_wrap(~block,labeller = as_labeller(split))+
  theme(strip.text = element_text(size=16))

```

look at eccentricity graphs (60-63): 
a. calculate absolute from center for x-coordinate  
b. slide 62,63 groups should be divided by preswitch aem groups

look at eccentricity: calculate absolute from center for x-coordinate for graphs (51,52,60-63)
screen res is 1024 x 1280 (Y X)
middle is 640
```{r}
#a. X axis = time, Y = x coordinate, lines = number of correct AEM preswitch
#make sure to know how many babies for each line
poo <- orig.sample8

#1. Binning every 100ms, to make sure that it's actually a fixation for lookstotarget
moo <- data.frame(subID=numeric(),trialnum=numeric(),timecode=numeric(),lookingattarget=numeric())
subs <- unique(poo$subID)
time <- seq(100,4000, by=100) #the time bins we are trying to create (0-4000ms) doing 4000ms bc s

for (j in 1:length(subs)) {
  #gets every trial for 1 subject
  trials <- unique(poo$TRIAL_INDEX[poo$subID==subs[j]])
  print(j)
  for (i in 1:length(trials)) {
  #gets all sample for 1 trial  
  woo <- subset(poo, subID==subs[j] & TRIAL_INDEX == trials[i])
  c <- woo$block[1]
  for (k in 1:length(time)){
    #for every 25 sample/100 ms, get lookattarget column
    if (k==1) {
    target <- woo$lookattarget[woo$TIMECODE < time[k]+1] #gets 0-100ms
    d <- unique(target)
    dd <- which(d==1)
    } else {
    target <- woo$lookattarget[woo$TIMECODE < time[k]+1 & woo$TIMECODE > time[k-1]-1]
    d <- unique(target)
    dd <- which(d==1)
    }
    #see if entire chunk is looking at target
    if (length(target)==0) { #no samples collected during this time
    aa <- c(subs[j],trials[i],c,time[k],99)   
    moo <- rbind(moo,aa)
    warnings()
    } else if (length(d)==1 & d==1) { #looking at target entire time
    aa <- c(subs[j],trials[i],c,time[k],d)   
    moo <- rbind(moo,aa)
    warnings()
    } else if (length(d)==1 & d==0) { #looking at distractor entire time
    aa <- c(subs[j],trials[i],c,time[k],d)   
    moo <- rbind(moo,aa)
    warnings()
    } else if (length(d)==1 & d==5) { #looking at center entire time
    aa <- c(subs[j],trials[i],c,time[k],d)   
    moo <- rbind(moo,aa)
    warnings()
    } else if (length(d) > 1 & length(dd) < 1) { #not looking at same location and not looking at target (looking at distractor and center)
    aa <- c(subs[j],trials[i],c,time[k],9)   
    moo <- rbind(moo,aa) 
    warnings()
    } else { #not looking at same location and but looking at target sometimes
    #calculate proportion looking  
    b <- length(which(target==1)) #samples where subs are looking at target
    bb <- length(which(target==1))/length(target) #looking at target/25
    aa <- c(subs[j],trials[i],c,time[k],bb) 
    moo <- rbind(moo,aa)
    warnings()
    }}}}

names(moo)[1] <- "subID"
names(moo)[2] <- "trialnum"
names(moo)[3] <- "block"
names(moo)[4] <- "timecode"
names(moo)[5] <- "lookattarget"
#0 = distractor, 1 = target, 5 = center, 9 = looking at distractor and center, 99 = no data collected

loo <- subset(moo, lookattarget == 1) #only care about AEMs to target/correct
loo$switch <- 1
loo$switch[loo$trialnum > 25] <- 2
loo$switch[loo$trialnum > 9 & loo$trialnum < 13 ] <- 2

loo2 <- subset(loo, switch==1) #only care about preswitch
hoo <- ddply(loo2,.(subID),summarise,numAEM=length(unique(trialnum)))
newData1 <- data.frame(subID = "7", numAEM = "0")
newData2 <- data.frame(subID = "16", numAEM = "0")
newData3 <- data.frame(subID = "27", numAEM = "0")

hoo <- rbind( hoo[1:6,], newData1, hoo[7:31,] )
hoo <- rbind( hoo[1:15,], newData2, hoo[16:32,] )
hoo <- rbind( hoo[1:26,], newData3, hoo[27:33,] )
hoo$numAEM <- as.numeric(hoo$numAEM)
which(hoo$numAEM==0) #16
which(hoo$numAEM==1) #3 11 22 24 30 31
which(hoo$numAEM==2) #29
which(hoo$numAEM==3) #2 13
which(hoo$numAEM==4) #5 14 19 21 28
which(hoo$numAEM==5) #1  4  8 12 15 17 18 20 32 33
which(hoo$numAEM==6) #6  9 10 23 25 26 34

#b. X coordinate timecourse, pre and post
boo <- subset(orig.sample8, switch==1)
boo$RIGHT_GAZE_X2 <- abs(boo$RIGHT_GAZE_X-640)

boo1 <- ddply(boo,.(subID,TIMECODE),summarise,xcoordinate=mean(RIGHT_GAZE_X2,na.rm = TRUE)) #collapse across trials
boo1$AEM <- 0
boo1$AEM[boo1$subID==3 | boo1$subID==11 |boo1$subID==22 |boo1$subID==24 |boo1$subID==30 |boo1$subID==31] <- 1
boo1$AEM[boo1$subID==29] <- 2
boo1$AEM[boo1$subID==2 | boo1$subID==13] <- 3
boo1$AEM[boo1$subID==5 | boo1$subID==14 |boo1$subID==19 |boo1$subID==21 |boo1$subID==28] <- 4
boo1$AEM[boo1$subID==1 | boo1$subID==4 |boo1$subID==8 |boo1$subID==12 |boo1$subID==15 |boo1$subID==17|boo1$subID==18|boo1$subID==20|boo1$subID==32|boo1$subID==33] <- 5
boo1$AEM[boo1$subID==6 | boo1$subID==9 |boo1$subID==10 |boo1$subID==23 |boo1$subID==25 |boo1$subID==26|boo1$subID==34] <- 6

boo2 <- ddply(boo1,.(AEM,TIMECODE),summarise,Xavg=mean(xcoordinate,na.rm = TRUE),seX=sd(xcoordinate, na.rm = TRUE)/sqrt(length(xcoordinate))) #collapse across subs
vlines <- c(250,1750,2550)

ggplot(boo2,aes(x=TIMECODE,y=Xavg,color=factor(AEM),fill=factor(AEM)))+
  geom_line()+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("Timecourse of X coordinate for preswitch")+
  labs(x = "Time", y = "Absolute distance from center")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  geom_ribbon(aes(ymin=Xavg-seX,ymax=Xavg+seX),alpha=0.4)+
  geom_vline(xintercept = vlines)+
  scale_x_continuous(limits=c(0,4000),breaks=seq(0,4000,500), expand = c(0, 0))+
  scale_y_continuous(limits=c(0,600),breaks=seq(0,600,100), expand = c(0, 0))+
  scale_fill_brewer(palette="Reds",name="Number of AEMs made during preswitch")+
  scale_color_brewer(palette="Reds")+
  guides(color=FALSE)+theme(legend.position = "bottom")

ggplot(boo2,aes(x=TIMECODE,y=Xavg))+
  geom_line()+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("Timecourse of X coordinate for preswitch")+
  labs(x = "Time", y = "Absolute distance from center")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  geom_ribbon(aes(ymin=Xavg-seX,ymax=Xavg+seX),alpha=0.4)+
  geom_vline(xintercept = vlines)+
  scale_x_continuous(limits=c(0,4000),breaks=seq(0,4000,500), expand = c(0, 0))+
  scale_y_continuous(limits=c(0,600),breaks=seq(0,600,100), expand = c(0, 0))+
  guides(color=FALSE)+facet_wrap(~AEM,ncol=2)

#b. do same for postswitch
boo <- subset(orig.sample8, switch==2)
boo$RIGHT_GAZE_X2 <- abs(boo$RIGHT_GAZE_X-640)

boo1 <- ddply(boo,.(subID,TIMECODE),summarise,xcoordinate=mean(RIGHT_GAZE_X2,na.rm = TRUE)) 
#labelling AEM according to how many they made during PRESWITCH
boo1$AEM <- 0
boo1$AEM[boo1$subID==3 | boo1$subID==11 |boo1$subID==22 |boo1$subID==24 |boo1$subID==30 |boo1$subID==31] <- 1
boo1$AEM[boo1$subID==29] <- 2
boo1$AEM[boo1$subID==2 | boo1$subID==13] <- 3
boo1$AEM[boo1$subID==5 | boo1$subID==14 |boo1$subID==19 |boo1$subID==21 |boo1$subID==28] <- 4
boo1$AEM[boo1$subID==1 | boo1$subID==4 |boo1$subID==8 |boo1$subID==12 |boo1$subID==15 |boo1$subID==17|boo1$subID==18|boo1$subID==20|boo1$subID==32|boo1$subID==33] <- 5
boo1$AEM[boo1$subID==6 | boo1$subID==9 |boo1$subID==10 |boo1$subID==23 |boo1$subID==25 |boo1$subID==26|boo1$subID==34] <- 6

boo2 <- ddply(boo1,.(AEM,TIMECODE),summarise,Xavg=mean(xcoordinate,na.rm = TRUE),seX=sd(xcoordinate, na.rm = TRUE)/sqrt(length(xcoordinate))) #collapse across subs
vlines <- c(250,1750,2550)

ggplot(boo2,aes(x=TIMECODE,y=Xavg,color=factor(AEM),fill=factor(AEM)))+
  geom_line()+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("Timecourse of X coordinate for postswitch")+
  labs(x = "Time", y = "Absolute distance from center")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  geom_ribbon(aes(ymin=Xavg-seX,ymax=Xavg+seX),alpha=0.4)+
  geom_vline(xintercept = vlines)+
  scale_x_continuous(limits=c(0,4000),breaks=seq(0,4000,500), expand = c(0, 0))+
  scale_y_continuous(limits=c(0,600),breaks=seq(0,600,100), expand = c(0, 0))+
  scale_fill_brewer(palette="Greens",name="Number of AEMs made during preswitch")+
  scale_color_brewer(palette="Greens")+
  guides(color=FALSE)+
  theme(legend.position = "bottom")

ggplot(boo2,aes(x=TIMECODE,y=Xavg))+
  geom_line()+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("Timecourse of X coordinate for postswitch")+
  labs(x = "Time", y = "Absolute distance from center")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  geom_ribbon(aes(ymin=Xavg-seX,ymax=Xavg+seX),alpha=0.4)+
  geom_vline(xintercept = vlines)+
  scale_x_continuous(limits=c(0,4000),breaks=seq(0,4000,500), expand = c(0, 0))+
  scale_y_continuous(limits=c(0,600),breaks=seq(0,600,100), expand = c(0, 0))+
  guides(color=FALSE)+facet_wrap(~AEM,ncol=2)

```

pupil timecourse for number of AEM
```{r}
#a. X axis = time, Y = x coordinate, lines = number of correct AEM preswitch
#make sure to know how many babies for each line
poo <- orig.sample8

#1. Binning every 100ms, to make sure that it's actually a fixation for lookstotarget
moo <- data.frame(subID=numeric(),trialnum=numeric(),timecode=numeric(),lookingattarget=numeric())
subs <- unique(poo$subID)
time <- seq(100,4000, by=100) #the time bins we are trying to create (0-4000ms) doing 4000ms bc s

for (j in 1:length(subs)) {
  #gets every trial for 1 subject
  trials <- unique(poo$TRIAL_INDEX[poo$subID==subs[j]])
  print(j)
  for (i in 1:length(trials)) {
  #gets all sample for 1 trial  
  woo <- subset(poo, subID==subs[j] & TRIAL_INDEX == trials[i])
  c <- woo$block[1]
  for (k in 1:length(time)){
    #for every 25 sample/100 ms, get lookattarget column
    if (k==1) {
    target <- woo$lookattarget[woo$TIMECODE < time[k]+1] #gets 0-100ms
    d <- unique(target)
    dd <- which(d==1)
    } else {
    target <- woo$lookattarget[woo$TIMECODE < time[k]+1 & woo$TIMECODE > time[k-1]-1]
    d <- unique(target)
    dd <- which(d==1)
    }
    #see if entire chunk is looking at target
    if (length(target)==0) { #no samples collected during this time
    aa <- c(subs[j],trials[i],c,time[k],99)   
    moo <- rbind(moo,aa)
    warnings()
    } else if (length(d)==1 & d==1) { #looking at target entire time
    aa <- c(subs[j],trials[i],c,time[k],d)   
    moo <- rbind(moo,aa)
    warnings()
    } else if (length(d)==1 & d==0) { #looking at distractor entire time
    aa <- c(subs[j],trials[i],c,time[k],d)   
    moo <- rbind(moo,aa)
    warnings()
    } else if (length(d)==1 & d==5) { #looking at center entire time
    aa <- c(subs[j],trials[i],c,time[k],d)   
    moo <- rbind(moo,aa)
    warnings()
    } else if (length(d) > 1 & length(dd) < 1) { #not looking at same location and not looking at target (looking at distractor and center)
    aa <- c(subs[j],trials[i],c,time[k],9)   
    moo <- rbind(moo,aa) 
    warnings()
    } else { #not looking at same location and but looking at target sometimes
    #calculate proportion looking  
    b <- length(which(target==1)) #samples where subs are looking at target
    bb <- length(which(target==1))/length(target) #looking at target/25
    aa <- c(subs[j],trials[i],c,time[k],bb) 
    moo <- rbind(moo,aa)
    warnings()
    }}}}

names(moo)[1] <- "subID"
names(moo)[2] <- "trialnum"
names(moo)[3] <- "block"
names(moo)[4] <- "timecode"
names(moo)[5] <- "lookattarget"
#0 = distractor, 1 = target, 5 = center, 9 = looking at distractor and center, 99 = no data collected

loo <- subset(moo, lookattarget == 1) #only care about AEMs to target/correct
loo$switch <- 1
loo$switch[loo$trialnum > 25] <- 2
loo$switch[loo$trialnum > 9 & loo$trialnum < 13 ] <- 2

loo2 <- subset(loo, switch==1) #only care about preswitch
hoo <- ddply(loo2,.(subID),summarise,numAEM=length(unique(trialnum)))
newData1 <- data.frame(subID = "7", numAEM = "0")
newData2 <- data.frame(subID = "16", numAEM = "0")
newData3 <- data.frame(subID = "27", numAEM = "0")

hoo <- rbind( hoo[1:6,], newData1, hoo[7:31,] )
hoo <- rbind( hoo[1:15,], newData2, hoo[16:32,] )
hoo <- rbind( hoo[1:26,], newData3, hoo[27:33,] )
hoo$numAEM <- as.numeric(hoo$numAEM)
which(hoo$numAEM==0) #16
which(hoo$numAEM==1) #3 11 22 24 30 31
which(hoo$numAEM==2) #29
which(hoo$numAEM==3) #2 13
which(hoo$numAEM==4) #5 14 19 21 28
which(hoo$numAEM==5) #1  4  8 12 15 17 18 20 32 33
which(hoo$numAEM==6) #6  9 10 23 25 26 34

#b. now get pupil info
boo <- subset(orig.sample8, switch==2)

boo1 <- ddply(boo,.(subID,TIMECODE),summarise,pupilsize=mean(PUPIL_CORRECTED,na.rm = TRUE)) 
#labelling AEM according to how many they made during PRESWITCH
boo1$AEM <- 0
boo1$AEM[boo1$subID==3 | boo1$subID==11 |boo1$subID==22 |boo1$subID==24 |boo1$subID==30 |boo1$subID==31] <- 1
boo1$AEM[boo1$subID==29] <- 2
boo1$AEM[boo1$subID==2 | boo1$subID==13] <- 3
boo1$AEM[boo1$subID==5 | boo1$subID==14 |boo1$subID==19 |boo1$subID==21 |boo1$subID==28] <- 4
boo1$AEM[boo1$subID==1 | boo1$subID==4 |boo1$subID==8 |boo1$subID==12 |boo1$subID==15 |boo1$subID==17|boo1$subID==18|boo1$subID==20|boo1$subID==32|boo1$subID==33] <- 5
boo1$AEM[boo1$subID==6 | boo1$subID==9 |boo1$subID==10 |boo1$subID==23 |boo1$subID==25 |boo1$subID==26|boo1$subID==34] <- 6

boo2 <- ddply(boo1,.(AEM,TIMECODE),summarise,pupilavg=mean(pupilsize,na.rm = TRUE),sepupil=sd(pupilsize, na.rm = TRUE)/sqrt(length(pupilsize))) #collapse across subs
vlines <- c(250,1750,2550)

ggplot(boo2,aes(x=TIMECODE,y=pupilavg,color=factor(AEM),fill=factor(AEM)))+
  geom_line()+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("Pupil timecourse for postswitch")+
  labs(x = "Time", y = "Pupil change (%)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  geom_ribbon(aes(ymin=pupilavg-sepupil,ymax=pupilavg+sepupil),alpha=0.4)+
  geom_vline(xintercept = vlines)+
  scale_x_continuous(limits=c(0,4000),breaks=seq(0,4000,500), expand = c(0, 0))+
  scale_fill_brewer(palette="Greens",name="Number of AEMs made during preswitch")+
  scale_color_brewer(palette="Greens")+
  guides(color=FALSE)+
  theme(legend.position = "bottom")+
  scale_y_continuous(labels=percent,limits=c(-0.4,.4),breaks=seq(-0.4,.4,.1), expand = c(0, 0))

ggplot(boo2,aes(x=TIMECODE,y=pupilavg))+
  geom_line()+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("Pupil timecourse for postswitch")+
  labs(x = "Time", y = "Pupil change (%)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  geom_ribbon(aes(ymin=pupilavg-sepupil,ymax=pupilavg+sepupil),alpha=0.4)+
  geom_vline(xintercept = vlines)+
  scale_x_continuous(limits=c(0,4000),breaks=seq(0,4000,500), expand = c(0, 0))+
  guides(color=FALSE)+facet_wrap(~AEM,ncol=2)+
  scale_y_continuous(labels=percent,limits=c(-0.4,.4),breaks=seq(-0.4,.4,.1), expand = c(0, 0))

```

